### 2019-03-08 PaperDraft.tex
add full paper draft

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{dsfont}
\usepackage{mathabx}
\usepackage[all, 2cell]{xy}
\usepackage[all]{xy}
\usepackage{wasysym}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{trfsigns}
\usepackage{cmll}
\usepackage{authblk}

\theoremstyle{defin}
\newtheorem{defin}{Definition}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}

\theoremstyle{prop}
\newtheorem{prop}{Proposition}

\theoremstyle{lemma}
\newtheorem{lemma}{Lemma}

\theoremstyle{ex}
\newtheorem{ex}{Example}

\theoremstyle{col}
\newtheorem{col}{Corollary}
\usepackage{listings} 		% for source code
\date{}
\author[1,2]{Daniel Rogozin}
\affil[1]{Lomonosov Moscow State University}
\affil[2]{Serokell O\"{U}}
\title{Models of Lambek calculus enriched with subexponentials}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{The Lambek Calculus with subexponentials}

\begin{defin} A subexponential signature is an ordered quintuple:

  $\Sigma = \langle I, \preceq, W, C, E \rangle$,
\end{defin}

where $I = \{ s_1, \dots, s_n\}$, $\langle I, \preceq \rangle$ is a preorder.
$W, C, E$ are upwardly closed subsets of $I$ and $W \cap C \subseteq E$.

\begin{defin}
$ $

  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | !_s \mathcal{F}_{\Sigma} $
\end{defin}

\begin{defin} Noncommutative linear logic with subexponentials ($SMALC_{\Sigma}$), where $\Sigma$ is a subexponential signature.

\begin{prooftree}
\AxiomC{$ $}
\RightLabel{\scriptsize{ax}}
\UnaryInfC{$A \rightarrow A$}
\end{prooftree}

\begin{minipage}{0.5\textwidth}
  \begin{flushleft}
    \begin{prooftree}
      \AxiomC{$\Gamma \rightarrow A$}
      \AxiomC{$\Delta, B, \Theta \rightarrow C$}
      \RightLabel{$\backslash \rightarrow$}
      \BinaryInfC{$\Delta, \Gamma, A \backslash B, \Theta \rightarrow C$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma \rightarrow A$}
      \AxiomC{$\Delta, B, \Theta \rightarrow C$}
      \RightLabel{$/ \rightarrow$}
      \BinaryInfC{$\Delta, B / A, \Gamma, \Theta \rightarrow C$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma, A, B, \Delta \rightarrow C$}
      \RightLabel{$\bullet \rightarrow$}
      \UnaryInfC{$\Gamma, A \bullet B, \Delta \rightarrow C$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma, A_i, \Delta \rightarrow B$}
      \RightLabel{$\&, i = 1,2 \rightarrow$}
      \UnaryInfC{$\Gamma, A_1 \& A_2, \Delta \rightarrow B$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma, A, \Delta \rightarrow C$}
      \AxiomC{$\Gamma, B, \Delta \rightarrow C$}
      \RightLabel{$\vee \rightarrow$}
      \BinaryInfC{$\Gamma, A \vee B, \Delta \rightarrow C$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma, \Delta \rightarrow A$}
      \RightLabel{${\bf 1} \rightarrow$}
      \UnaryInfC{$\Gamma, {\bf 1}, \Delta \rightarrow A$}
    \end{prooftree}

    \begin{prooftree}
    \AxiomC{$\Gamma, A, \Delta \rightarrow C$}
    \RightLabel{$! \rightarrow$}
    \UnaryInfC{$\Gamma, !^{s} A, \Delta \rightarrow C$}
    \end{prooftree}
  \end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
  \begin{flushright}
    \begin{prooftree}
      \AxiomC{$A, \Pi \rightarrow B$}
      \RightLabel{$\rightarrow \backslash$}
      \UnaryInfC{$\Pi \rightarrow A \backslash B$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Pi, A \rightarrow B$}
      \RightLabel{$\rightarrow /$}
      \UnaryInfC{$\Pi \rightarrow B / A$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma \rightarrow A$}
      \AxiomC{$\Delta \rightarrow B$}
      \RightLabel{$\rightarrow \bullet$}
      \BinaryInfC{$\Gamma, \Delta \rightarrow A \bullet B$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma \rightarrow A$}
      \AxiomC{$\Gamma \rightarrow B$}
      \RightLabel{$\rightarrow \&$}
      \BinaryInfC{$\Gamma \rightarrow A \& B$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma \rightarrow A_i$}
      \RightLabel{$\rightarrow \vee, i = 1,2$}
      \UnaryInfC{$\Gamma \rightarrow A_1 \vee A_2$}
    \end{prooftree}

    \begin{prooftree}
      \AxiomC{$ $}
      \RightLabel{$\rightarrow {\bf 1}$}
      \UnaryInfC{$\rightarrow {\bf 1}$}
    \end{prooftree}

    \begin{prooftree}
    \AxiomC{$!^{s_1} A_1, \dots, !^{s_n} A_n \rightarrow A$}
    \RightLabel{$\rightarrow !, \forall j, s_j \succeq s$}
    \UnaryInfC{$!^{s_1} A_1, \dots, !^{s_n} A_n \rightarrow !^{s} A$}
    \end{prooftree}
  \end{flushright}
\end{minipage}
Structural rules:

\begin{minipage}{0.5\textwidth}
  \begin{flushleft}
        \begin{prooftree}
        \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
        \RightLabel{${\bf ncontr}_1, s \in C$}
        \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
        \end{prooftree}

        \begin{prooftree}
        \AxiomC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
        \RightLabel{${\bf ex}_1, s \in E$}
        \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow A$}
        \end{prooftree}

    \begin{prooftree}
      \AxiomC{$\Gamma, \Delta \rightarrow B$}
      \RightLabel{${\bf weak}_!, s \in C$}
      \UnaryInfC{$\Gamma, !^{s} A, \Delta \rightarrow B$}
    \end{prooftree}

  \end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
  \begin{flushright}

      \begin{prooftree}
        \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
        \RightLabel{${\bf ncontr}_2, s \in C$}
        \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
      \end{prooftree}

      \begin{prooftree}
        \AxiomC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
        \RightLabel{${\bf ex}_2, s \in E$}
        \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow A$}
      \end{prooftree}

  \begin{prooftree}
    \AxiomC{$\Gamma \rightarrow A$}
    \AxiomC{$\Pi, A, \Delta \rightarrow B$}
    \RightLabel{${\bf cut}$}
    \BinaryInfC{$\Gamma, \Pi, \Delta \rightarrow B$}
  \end{prooftree}
  \end{flushright}
\end{minipage}
\end{defin}

\begin{theorem}
$ $

  \begin{enumerate}
    \item Cut-rule is admissable;
    \item $\text{SMALC}_{\Sigma}$ is undecidable, if $C \neq \emptyset$;
    \item If $C$ is empty, then the decidability problem of $\text{SMALC}_{\Sigma}$ belongs to PSPACE.
  \end{enumerate}
\end{theorem}

\section{Semantics}

\begin{defin} Quantale
$ $

  A quantale is a triple $\langle A, \bigvee, \cdot \rangle$, such that $\langle A, \bigvee \rangle$
is a complete lattice and $\langle A, \cdot \rangle$ is a semigroup. A quanlate is called unital, if $\langle A, \cdot \rangle$
is a monoid.
\end{defin}

Some example of quantales:

\begin{itemize}
\item Let $A$ be a semigroup (monoid), then $\langle \mathcal{P}(A), \cdot, \subseteq \rangle$
is a free (unital) quantale.
\item Let $R$ be a ring and $Sub(R)$ be a set of additive subgroups of $R$.
We define $A \cdot B$ as an additive subgroup generated by finite sums of products $ab$ and order is defined by inclusion.
\item Any locale is a quantale with $\cdot = \wedge$.
\end{itemize}

It is easy to see, that any (unital) quantale is a residual (monoid) semigroup. We define divisions as follows:

\begin{enumerate}
\item $a \backslash b = \bigvee \{ c \: | \: a \cdot c \leq b \}$
\item $b / a = \bigvee \{ c \: | \: c \cdot a \leq b \}$
\end{enumerate}

\begin{defin}
$ $

  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale. The center of a quantale is the set $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
\end{defin}

\begin{defin} An open modality (or quantic conucleus) on quantale $\mathcal{Q}$ is a map $\Box : \mathcal{Q} \to \mathcal{Q}$, such that

\begin{enumerate}
  \item $\Box x \leq x$;
  \item $\Box x = \Box \Box x$;
  \item $x \leq y \Rightarrow \Box x \leq \Box y$;
  \item $\Box x \cdot \Box y = \Box (\Box x \cdot \Box y)$.
\end{enumerate}
\end{defin}

For unital quantale, we require that $\Box e = e$.

Note that, we may replace the last condition on equivalent condition $\Box (x) \cdot \Box (y) \leq \Box (x \cdot y)$.

\begin{defin}
  We define a partial order on open modalities on $\mathcal{Q}$ as $\Box_1 \leq \Box_2 \Leftrightarrow \forall a \in Q, \Box_1 (a) \leq \Box_2 (a)$.
\end{defin}

\begin{lemma}
  Let $\mathcal{Q}$ be a quantale and $\Box_{\mathcal{Q}}$ be a set of all open modalities on $\mathcal{Q}$.
  Then $\Box_{\mathcal{Q}}$ is a small category.
\end{lemma}

\begin{proof}
  $\langle \Box_{\mathcal{Q}}, \leq \rangle$ form a partial order, so $\langle \Box_{\mathcal{Q}}, \leq \rangle$ is a small category.
\end{proof}

\begin{defin}
$ $
\begin{enumerate}
  \item An open modality is called central, if $\forall a, b \in Q, \Box(a) \cdot b = b \cdot \Box(a)$.

  \item An open modality is called pseudo-idempotent, if $\forall a, b \in Q, \Box(a) \cdot b \leq \Box(a) \cdot b \cdot \Box(a)$ and
  $b \cdot \Box(a) \leq \Box(a) \cdot b \cdot \Box(a)$.

  \item An open modality is called unital, if $\forall a \in Q, \Box(a) \leq e$.
\end{enumerate}
\end{defin}

\begin{lemma}
  Let $\Box$ be an open modality on some unital quantale $\mathcal{Q} = \langle A, \bigvee, \cdot, e \rangle$.
  Then, if $\Box$ is unital and weak idempotent, then $\Box$ is central.
\end{lemma}

\begin{proof}
$ $

  $\begin{array}{lll}
  & b \cdot \Box(a) \leq & \\
  & \:\:\:\: \text{Right weak idempotence}& \\
  &\Box(a) \cdot b \cdot \Box(a) \leq & \\
  & \:\:\:\: \text{Unitality}& \\
  & \Box(a) \cdot b \cdot e \leq & \\
  & \:\:\:\: \text{Identity}& \\
  &\Box(a) \cdot b \leq & \\
  & \:\:\:\: \text{Left weak idempotence}& \\
  &\Box(a) \cdot b \cdot \Box(a) \leq & \\
  & \:\:\:\: \text{Unitality}& \\
  &e \cdot b \cdot \Box(a) \leq & \\
  & \:\:\:\: \text{Identity}& \\
  &b \cdot \Box(a)&
  \end{array}$

Hence, $b \cdot \Box(a) = \Box(a) \cdot b$, so $\forall a \in A, \Box(a) \in \mathcal{Z}(\mathcal{Q})$.

\end{proof}

\begin{prop}
$ $

  Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale, then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that
$\Box(a) = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
\end{prop}

\begin{proof}
  See
\end{proof}

\begin{prop}
$ $

  Let $\mathcal{Q}$ be a quantale and $S_1 \subseteq S_2 \subseteq \mathcal{Q}$.

  Then $\Box_1 (a) \leq \Box_2 (a)$.
\end{prop}

\begin{proof}

Immediatly.
\end{proof}

\begin{prop}
$ $

Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale, then the following operations are open modalities:

\begin{enumerate}
  \item $\Box_z (a) = \bigvee \{ s \in S \: | s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \}$;
  \item $\Box_{\mathds{1}} (a) = \bigvee \{ s \in S \: | s \leq a, s \leq \mathds{1} \}$;
  \item $\Box_{idem} (a) = \bigvee \{ s \in S \: | s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$;
  \item $\Box_{z, \mathds{1}}, I_{z, idem}, I_{\mathds{1}, idem}, I_{z, \mathds{1}, idem}$.
\end{enumerate}
\end{prop}

\begin{proof}
  Immediatly.
\end{proof}

\begin{prop}
$ $

\begin{enumerate}
  \item $\forall a \in \mathcal{Q}, \Box_{\mathds{1}, idem}(a) \leq \Box_z (a)$.
  \item $\forall a \in \mathcal{Q}, \Box_{z, \mathds{1}, idem} = \Box_{\mathds{1}, idem}(a)$
\end{enumerate}

\end{prop}

\begin{proof}
  Follows from Lemma 3.
\end{proof}

\begin{lemma}
  $\Box_1(a_1) \cdot \Box_2(a_2) \leq \Box^{'} (\Box_1(a_1) \cdot \Box_2(a_2))$, where $\Box_i \leq \Box^{'}, i = 1,2$.
\end{lemma}

\begin{proof}
$ $

  $\begin{array}{lll}
  &\Box_1(a_1) \cdot \Box_2(a_2) \leq & \\
  &\Box_1 (\Box_1 (a_1)) \cdot \Box_2 (\Box_2 (a_2)) \leq & \\
  &\Box^{'} (\Box_1 (a_1)) \cdot \Box^{'} (\Box_2 (a_2)) \leq & \\
  &\Box^{'}(\Box_1 (a_1) \cdot \Box_2 (a_2))&
  \end{array}$
\end{proof}

\begin{defin} Interpretation of subexponential signature

  Let $\Sigma = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature, where $|I| = n$ and
  $\Box_{\mathcal{Q}}$ is a category of open modalities on a quantale $\mathcal{Q}$.
  Subexponential interpretation is a contravariant functor $\sigma : I \to \Box_{\mathcal{Q}}$ defined as follows:

  $\sigma(s_i) = \begin{cases}
  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a\},
  \\ \:\:\:\: \text{if $s_i \notin W \cap C \cap E$} \\
  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
  \\ \:\:\:\: \text{if $s_i \in W$} \\
  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
  \\ \:\:\:\: \text{if $s_i \in E$} \\
  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
  \\ \:\:\:\: \text{if $s_i \in E$} \\
  \text{otherwise, if $s_i$ belongs to some intersection of subsets, then we combine the relevant conditions } \\
  \end{cases}$
\end{defin}

\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : I \to \Box_{\mathcal{Q}}$ a subexponential interpretation, then
  interpretation is defined inductively:

\begin{center}
$\begin{array}{lll}
& [\![p_i]\!] = f(p_i)&\\
& [\![\mathds{1}]\!] = e & \\
&[\![A \bullet B]\!] = [\![A]\!] \cdot [\![B]\!] & \\
&[\![A \backslash B]\!] = [\![A]\!] \backslash [\![B]\!] & \\
&[\![A / B]\!] = [\![A]\!] / [\![B]\!]& \\
&[\![A \& B]\!] = [\![A]\!] \wedge [\![B]\!]& \\
&[\![A \vee B]\!] = [\![A]\!] \vee [\![B]\!]& \\
&[\![!_{s_i} A]\!] = \sigma(s_i) [\![A]\!]&
\end{array}$
\end{center}
\end{defin}

\begin{defin}
  $\Gamma \models A \Leftrightarrow \forall f, \forall \sigma, [\![\Gamma]\!] \leq [\![A]\!]$
\end{defin}

\begin{theorem}
  $\Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$
\end{theorem}

\begin{proof}
We consider the promotion case, the rest modal cases are immediatly shown.

Let $!_{s_1} A_1, \dots, !_{s_n} A_n \rightarrow A$ and $\forall i, s \preceq s_i$.

Then $\forall a \in Q, \sigma(s_i)(a) \leq \sigma(s)(a)$.

By IH, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq [\![A]\!]$.

Thus, $\sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!]) \leq \sigma(s)([\![A]\!])$.

By Lemma 5, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!])$.

So, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)([\![A]\!])$.
\end{proof}

\section{Quantale completeness}

\begin{defin}
$ $

  Let $\mathcal{F} \subseteq Fm$, an ideal is a subset $\mathcal{I} \subseteq \mathcal{F}$, such that:

\begin{itemize}
  \item If $B \in \mathcal{I}$ and $A \rightarrow B$, then $A \in \mathcal{I}$;
  \item If $A, B \in \mathcal{I}$, then $A \lor B \in \mathcal{I}$.
\end{itemize}
\end{defin}

\begin{defin}
$ $

  Let $S \subseteq \mathcal{F} \subseteq Fm$,
  then $\bigvee S = \bigcap \{ \mathcal{I} \subseteq \mathcal{F} \: | \: S \subseteq \mathcal{I} \}$
\end{defin}

\begin{prop}
  $\bigvee S$ is an ideal.
\end{prop}

\begin{lemma}
  $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$.
\end{lemma}

\begin{proof}
$ $

Let $A \in Fm$. Then $\{ B \: | \: B \rightarrow A', A' \in A \} \subseteq \bigvee \{ A \}$,
so far as $\bigvee A$ is an ideal.

On the other hand, $\{ B \: | \: B \rightarrow A \}$ is an ideal, it is easy to see that this set is closed under $\lor$.
So, $\bigvee A \subseteq \{ B \: | \: B \rightarrow A \}$.
\end{proof}

\begin{lemma}
  $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$.
\end{lemma}

\begin{proof}
  Let $\bigvee \{ A \} \subseteq \bigvee \{ B \}$,
  then $\{ C | C \rightarrow A \} \subseteq \{ D \: | \: D \rightarrow B \}$.

Thus, $A \in \{ C | C \rightarrow A \}$,
then $A \in \{ D \: | \: D \rightarrow B \}$, hence $A \rightarrow B$.

On the other hand, let $A \rightarrow B$ and $C \in \bigvee \{ A \}$.

Thus, $C \rightarrow A$, then $C \rightarrow B$ by cut.

\end{proof}

\begin{lemma}
  Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a quantale.
\end{lemma}

\begin{proof}
  See
\end{proof}

\begin{lemma}
  Let $!_s \in I$ and $A$ be an arbitrary formula, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ B \: | \: !_s B \rightarrow A \}$
  is a quantic conucleus.
\end{lemma}

\begin{proof}
$ $

See Yetter.
\end{proof}

\begin{lemma}
  Let $A$ be a formula, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$.
\end{lemma}

\begin{proof}
  Let $A \in Fm$ and $s \in \mathcal{I}$.

  Let $!_s B \in \Box_s \bigvee \{ A \}$, then $!_s B \rightarrow A$, then $!_s B \rightarrow !_s A$
  by promotion. So, $!_s B \in \bigvee \{ !_s A \}$.

  Let $C \in \bigvee \{ !_s A \}$, then $C \rightarrow !_s A$, so $!_s C \rightarrow !_s A$ by dereliction, but $!_s A \rightarrow A$, hence
  $!_s C \rightarrow A$ by cut. So, $!_s C \in \Box_s \bigvee \{ A \}$.
\end{proof}

\begin{lemma}
$ $

  Let $i, j \in I$ and $i \preceq j$, then for all $A \in Fm$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
\end{lemma}

\begin{proof}
$ $

  Let $i, j \in I$ and $i \preceq j$. Then forall $A \in Fm$, $!_j A \rightarrow !_i A$ by promotion.
  Then $\bigvee \{ !_j A \} \subseteq \bigvee \{ !_i A \}$, so $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
\end{proof}

\begin{lemma}
$ $

  \begin{enumerate}
    \item Let $s \in W$, then for all $A \subseteq Fm$, $\Box_s \{ A \} \subseteq \{ {\bf 1} \}$;
    \item Let $s \in E$, then $\Box_s (\bigvee \{ A \}) \cdot \bigvee \{ B \} = \bigvee \{ B\} \cdot \Box_s (\bigvee \{ A \})$.
    \item Let $s \in C$, then $(\Box_s \bigvee A \cdot \bigvee B) \cup (\bigvee B \cdot \Box_s \bigvee A) \subseteq \Box_s \bigvee A \cdot \bigvee B \cdot \Box_s \bigvee A$, for all $B \subseteq Fm$.
  \end{enumerate}
\end{lemma}

\begin{proof}
$ $

  \item Follows from $!_s A \rightarrow {\bf 1}$, so $s \in W$;
  \item Follows from $!_s A \bullet B \leftrightarrow B \bullet !_s A$;
  \item Follows from $!_s A \bullet B \rightarrow !_s A \bullet B \bullet !_s A$ and similarly for $B \bullet !_s A$.
\end{proof}

\begin{defin}
$ $

Let $Q$ be a syntactic quantale as proposed above and
$\mathcal{I} = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature.

We define a map $\Box : \mathcal{I} \to Mod_{\mathcal{Q}}$ as follows:

$\Box(i)(\bigvee \{ A \} ) = \{ !_i B \: | !_i B \rightarrow A \}$.
\end{defin}

\begin{lemma} $\Box$ is a subexponential interpretation.
\end{lemma}

\begin{proof}
  Follows from lemmas above.
\end{proof}

\begin{lemma}
$ $

  Let $Q$ be a quantale constructed above and $\Box_1, \dots, \Box_n$ be a family of quantic conuclei on $Q$.
  Then there exist a model $\langle Q, [\![.]\!]\rangle$, such that $[\![A]\!] = \bigvee \{ A \}$, $A \in Fm$.
\end{lemma}

\begin{proof}
$ $

  We define an interpreation as follows:

\begin{enumerate}
  \item $[\![p_i]\!] = \bigvee \{ p_i \}$
  \item $[\![{\bf 1}]\!] = \bigvee \{ {\bf 1} \}$
  \item $[\![A \bullet B]\!] = \bigvee \{ A \bullet B \}$
  \item $[\![A / B]\!] = \bigvee \{ A / B \}$
  \item $[\![B \setminus A]\!] = \bigvee \{ B \setminus A \}$
  \item $[\![A \& B ]\!] = \bigvee \{ A \& B \}$
  \item $[\![A \lor B]\!] = \bigvee \{ A \lor B\}$
  \item $[\![!_s A]\!] = \Box(s) (\bigvee \{ A \}) = \bigvee \{ !_s A \}$.
\end{enumerate}
\end{proof}

\begin{theorem}
  $\Gamma \models A \Rightarrow \Gamma \rightarrow A$.
\end{theorem}

\begin{proof}
  Follows from lemmas above.
\end{proof}

\begin{defin} Monoidal comonad
  $ $

  A monoidal comonad on some monoidal category $\mathcal{C}$ is a triple $\langle \mathcal{F}, \epsilon, \delta \rangle$,
  where $\mathcal{F}$ is a monoidal endofunctor and $\epsilon : \mathcal{F} \Rightarrow Id_{\mathcal{C}}$ (counit) and $\epsilon : \mathcal{F} \Rightarrow \mathcal{F}^2$ (comultiplication),
  such that the following diagrams commute:

\begin{minipage}{0.45\textwidth}
\begin{small}
\xymatrix{
\mathcal{F}A \otimes \mathcal{F}B \ar[dd]_{\delta_A \otimes \delta_B} \ar[r]^{\phi_{A,B}} & \mathcal{F}(A \otimes B) \ar[dr]^{\delta_{A \otimes B}} \\
&& \mathcal{F}\mathcal{F}(A \otimes B) \\
\mathcal{F}\mathcal{F}A \otimes \mathcal{F}\mathcal{F}B \ar[r]_{\phi_{\mathcal{F}A, \mathcal{F}B}} & \mathcal{F}(\mathcal{F}A \otimes \mathcal{F}B) \ar[ur]_{\mathcal{F}(\phi_{A,B})}
}
\end{small}
\end{minipage}%
\hfill
\begin{minipage}{0.5\textwidth}
\begin{tabular}{p{\textwidth}}
\xymatrix{
\mathcal{F}A \otimes \mathcal{F}B \ar[rr]^{\phi_{A,B}} \ar[dr]_{\epsilon_A \otimes \epsilon_B} && \mathcal{F}(A \otimes B) \ar[dl]^{\epsilon_{A \otimes B}} \\
& A \otimes B &
}
\end{tabular}
\end{minipage}%

\xymatrix{
&&&&&&& \mathds{1} \ar[r]^{\phi} \ar[d]_{\phi} & \mathcal{F}\mathds{1} \ar[d]^{\delta_{\mathds{1}}} \\
&&&&&&& \mathcal{F}\mathds{1} \ar[r]_{\mathcal{F}(\phi)} & \mathcal{F}\mathcal{F}\mathds{1}
}

\xymatrix{
&&&&&&& \mathds{1} \ar[dr]_{\phi} \ar[rr]^{id_{\mathds{1}}} && \mathds{1}\\
&&&&&&&& \mathcal{F}\mathds{1} \ar[ur]_{\epsilon_{\mathds{1}}} &
}
\end{defin}

\begin{defin} Biclosed monoidal category

  Let $\mathcal{C}$ be a monoidal category. Biclosed monoidal category is a monoidal category with the following additional data:
  \begin{enumerate}
    \item Bifunctors $\underline{\quad} \multimapinv \underline{\quad}, \underline{\quad} \multimap \underline{\quad} : \mathcal{C}^{op} \times \mathcal{C} \to \mathcal{C}$;
    \item Natural isomophism ${\bf curry}_{A,B,C} : Hom (A \otimes B, C) \cong (B, A \multimap C)$;
    \item Natural isomophism ${\bf curry}^{'}_{A,B,C} : Hom (A \otimes B, C) \cong (A, C \multimap B)$;
    \item For each $A, B \in Ob_{\mathcal{C}}$, there are exist arrows $ev_{A,B} : A \otimes (A \Rightarrow B) \rightarrow B$ and $ev_{A,B}^{'} : (B \Leftarrow A) \otimes A \rightarrow B$,
    such that for all $f : A \otimes C \rightarrow B$:
      \begin{enumerate}
        \item $\Lambda_l \circ (id_A \otimes {\bf curry}(f)) = f$;
        \item $\Lambda_r \circ ({\bf curry}^{'}(f) \otimes id_A) = f$
      \end{enumerate}
  \end{enumerate}
\end{defin}

\begin{defin}
  Let $F$ be endofunctor and $A \in Ob\mathcal{C}$, then a coalgebra of $F$ is a tuple $\langle A, \theta \rangle$, where $\theta : A \to F A$.
\end{defin}

Given coalgebras $\langle A, \theta \rangle$ and $\langle A, \psi \rangle$, a homomorphism is a morphism $f : A \to B$, s.t. the diagram below commutes:

\xymatrix{
&&&&&& A \ar[dd]_{f} \ar[rr]^{\theta} && F A \ar[dd]^{F f} \\
\\
&&&&&& B \ar[rr]_{\psi} && F B
}
that is, $F f \circ \theta = \psi \circ f$

\begin{defin} Subexponential model structure

  Let $\Sigma = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature and $\mathcal{C}$ be a biclosed monoidal category,
  then a subexponential model structure is $\langle \mathcal{C}, \{ \mathcal{F}_{s} \}_{s \in I} \rangle$ with the following additional data:

\begin{itemize}
  \item for all $s \in I$, $\mathcal{F}_s$ is a monoidal comonad;
  \item if $s \in W$, then for all $A \in Ob(\mathcal{C})$, there exists a morphism ${w_{A}}_{s} : F_s A \to \mathds{1}$;
  \item if $s \in C$, then for all $A \in Ob(\mathcal{C})$, there exists morphisms
${w_{A}}_{l} : F_s A \otimes A \otimes F_s A \to F_s A \otimes B$ and ${w_{A}}_{r} : F_s A \otimes A \otimes F_s A \to B \otimes F_s A$;
  \item if $s \in E$, then for all $A \in Ob(\mathcal{C})$, there is an isomorpism, ${e_A} : F_s A \otimes B \cong B \otimes F_s A$;
  \item if $s_1 \in W$, $s_2 \in I$ and $s_1 \preceq s_2$, then there is a morphism ${w_{A}}_{s_2} : F_{s_2} A \to \mathds{1}$ for all $A \in Ob(\mathcal{C})$ and ditto for $E$ and $C$;
  \item Let $\bigotimes_{s \in J, i = 0}^{n} F_{s} A$, where $J \subset I$, and $s^{'} \in I$, s.t. $s \succeq s^{'}$ for all $s \in I'$;
  Then there exists morphism a morphism $\theta_{\bigotimes_{s \in J, i = 1}^{n} {F_{s}}_j A_i} : \bigotimes_{s \in J, i = 0}^{n} F_{s} A \to F_{s^{'}} (\bigotimes_{s \in J, i = 0}^{n} F_{s} A)$, such that
  $\langle \bigotimes_{s \in J, i = 1}^{n} {F_{s}}_j A_i, \theta_{\bigotimes_{s \in J, i = 1}^{n} {F_{s}}_j A_i} \rangle$ is a coalgebra on $F_s$.
\end{itemize}
\end{defin}

\begin{defin}
  Let $\langle \mathcal{C}, \{ \mathcal{F}_{s} \}_{s \in I} \rangle$ be a subexponential model structure
  for subexponential signature $\Sigma = \langle I, \preceq, W, C, E \rangle$.
  Let $v : Tp \to Ob(\mathcal{C})$ be a valuation map. Then the interpretation function $[\![.]\!]$ is defined as follows:

$\begin{array}{lll}
(1) &[\![{\bf 1}]\!] = \mathds{1}& \\
(2) &[\![A \backslash B]\!] = [\![A]\!] \multimap [\![B]\!]& \\
(3) &[\![A / B]\!] = [\![A]\!] \multimapinv [\![B]\!]& \\
(4) &[\![A \bullet B]\!] = [\![A]\!] \otimes [\![B]\!]&\\
(5) &[\![!_{s} A]\!] = F_s [\![A]\!]& \\
\end{array}$
\end{defin}

\begin{theorem} The following statements are equivalent:

  \begin{itemize}
    \item $SMLC_{\Sigma} + (cut) \vdash \Gamma \Rightarrow A$
    \item $SMLC_{\Sigma} \vdash \Gamma \Rightarrow A$
    \item $\exists f, f : [\![\Gamma]\!] \rightarrow [\![A]\!]$
  \end{itemize}
\end{theorem}

\begin{proof}
  \begin{itemize}
$ $

    \item (1) $\Rightarrow$ (2): cut elimination.
    \item (2) $\Rightarrow$ (3): Soundness:

\begin{prooftree}
  \AxiomC{$f : \Gamma \otimes A \otimes \Delta \rightarrow B$}
  \UnaryInfC{$f \circ (id_{\Gamma} \otimes \delta_s^{A} \otimes id_{\Delta}) : \Gamma \otimes F_s A \otimes \Delta \rightarrow B$}
\end{prooftree}

\begin{prooftree}
  \AxiomC{$f : F_{s_1} A_1 \otimes \dots \otimes F_{s_n} A_n \rightarrow B$}
  \UnaryInfC{$F_s(f) : F_s(F_{s_1} A_1 \otimes \dots \otimes F_{s_n} A_n) \rightarrow F_s B$}
  \UnaryInfC{$F_s (f) \circ \theta_{\bigotimes_{s \in J, i = 1}^{n} {F_{s}}_j A_i} : F_{s_1} A_1 \otimes \dots \otimes F_{s_n} A_n \rightarrow F_s B$}
\end{prooftree}

\begin{prooftree}
  \AxiomC{$f : \Gamma \otimes \Delta \rightarrow A$}
  \UnaryInfC{$f \circ (\rho_{\Gamma} \otimes id_{\Delta}) : (\Gamma \otimes \mathds{1}) \otimes \Delta \rightarrow A$}
  \UnaryInfC{$f \circ (\rho_{\Gamma} \otimes id_{\Delta}) \circ (id_{\Gamma} \otimes {w_{A}}_{s}) \otimes id_{\Delta} : (\Gamma \otimes F_s A) \otimes \Delta \rightarrow A$}
\end{prooftree}

\begin{prooftree}
  \AxiomC{$f : \Gamma \otimes (F_s A \otimes B \otimes F_s A) \otimes \Delta \rightarrow C$}
  \UnaryInfC{$f \circ (id_{\Gamma} \otimes {c_A}_{s}^l \otimes id_{\Delta}) : \Gamma \otimes (F_s A \otimes B) \otimes \Delta \rightarrow C$}
\end{prooftree}

\begin{prooftree}
  \AxiomC{$f : \Gamma \otimes (F_s A \otimes B \otimes F_s A) \otimes \Delta \rightarrow C$}
  \UnaryInfC{$(id_{\Gamma} \otimes {c_A}_{s}^r \otimes id_{\Delta}) \circ f: \Gamma \otimes (B \otimes F_s A) \otimes \Delta \rightarrow C$}
\end{prooftree}

\begin{prooftree}
  \AxiomC{$f : \Gamma \otimes (\Delta \otimes F_s A) \otimes \Theta \rightarrow B$}
  \UnaryInfC{$(id_{\Gamma} \otimes (id_{\Delta} \otimes {e_A}_{s}) \otimes id_{\Theta}) \circ f: \Gamma \otimes (F_s A \otimes \Delta) \otimes \Theta \rightarrow B$}
\end{prooftree}

\begin{prooftree}
  \AxiomC{$f : \Gamma \otimes (F_s A \otimes \Delta) \otimes \Theta \rightarrow B$}
  \UnaryInfC{$(id_{\Gamma} \otimes (id_{\Delta} \otimes {e_A}_{s}^{-1}) \otimes id_{\Theta}) \circ f: \Gamma \otimes (\Delta \otimes F_s A) \otimes \Theta \rightarrow B$}
\end{prooftree}

    \item Completeness:

\begin{defin}
\end{defin}

  \end{itemize}
\end{proof}

\section{Relational semantics}

\begin{defin}
  $ $

  Let $A$ be a set. Then relational quantale on $A$ is a tuple $\mathcal{Q} = \langle \mathcal{A}, \mathcal{I} \rangle$
  where $\mathcal{A} \subseteq 2^{A \times A}$:

  \begin{itemize}
    \item $\langle \mathcal{A}, \subseteq \rangle$ is a complete semi-lattice;
    \item Multiplication is defined as
      $R \circ S = \{ \langle a, c \rangle \: | \: \exists b \in A, \langle a, b \rangle \in R \text{ and } \langle b, c \rangle \in S\}$
    \item $\langle \mathcal{A}, \circ, \mathcal{I} \rangle$ is a monoid;
    \item For each indexing set $J$, $R \circ \bigvee_{j \in J} S_j = \bigvee_{j \in J} (R \circ S_j)$ and
      $\bigvee_{j \in J} R_j \circ S = \bigvee_{j \in J}(R_j \circ S)$.
  \end{itemize}
\end{defin}

Let us define forcing relation $\Vdash$ between elements of $\mathcal{Q}$ and types as follows for arbitrary valuation map $w : Tp \to \mathcal{A}$:
\begin{enumerate}
  \item Let $p_i \in Tp$, then $\langle a, b \rangle \Vdash p_i \Leftrightarrow \langle a, b \rangle \in w(p_i)$;
  \item $\langle a, b \rangle \Vdash {\bf 1} \Leftrightarrow \langle a, b \rangle \in \mathcal{I}$;
  \item $\langle a, b \rangle \Vdash A \backslash B \Leftrightarrow \forall c \in A, \langle c, a \rangle \Vdash A \Rightarrow \langle c, b \rangle \Vdash A$;
  \item $\langle a, b \rangle \Vdash B / A \Leftrightarrow \forall c \in A, \langle a, c \rangle \Vdash A \Rightarrow \langle b, c \rangle \Vdash A$;
  \item $\langle a, b \rangle \Vdash A \bullet B \Leftrightarrow \exists c, \langle a, c \rangle \Vdash A \text{ and } \langle c, b \rangle \Vdash B$;
  \item $\langle a, b \rangle \Vdash A \lor B \Leftrightarrow \langle a, b \rangle \Vdash A \text{ or } \langle a, b \rangle \Vdash B$;
  \item $\langle a, b \rangle \Vdash A \& B \Leftrightarrow \langle a, b \rangle \Vdash A \text{ and } \langle a, b \rangle \Vdash B$;
  \item $\langle a, b \rangle \Vdash !A \Leftrightarrow \exists S_{\langle a, b \rangle} \forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$
  \item $\langle a, b \rangle \Vdash \Gamma \rightarrow A \Leftrightarrow \langle a,b \rangle \Vdash A_1 \bullet \dots \bullet A_n \Rightarrow  \langle a,b \rangle \vdash A$;
\end{enumerate}

Example:

\begin{itemize}
Let us show that $\mathcal{Q} \models !A \rightarrow A$.

Let $\mathcal{Q} \models !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
Hence there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$,
but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \models A$.

\item Let us show that $\mathcal{Q} \models !A \rightarrow !!A$.

Let $\langle a, b \rangle \models !A$. Let us show that $\langle a, b \rangle \models !!A$.

So there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$.

Let $S' \subseteq S_{\langle a, b \rangle}$, then for each $\langle a', b' \rangle \in S', \langle a', b' \rangle \Vdash A$,
so $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models !A$, so  $\langle a, b \rangle \models !!A$.
\end{itemize}

\begin{theorem}

  Let $\langle A \rangle$
\end{theorem}

\begin{theorem}
$ $

  Let $\mathcal{Q}$ be a relational quantale, then $Log(\mathcal{Q}) = L^{*}(\backslash, /, \bullet, {\bf 1}, \&, \vee)$.
\end{theorem}

\end{document}

### 2019-03-09 PaperDraft.tex
updates

@@
 
-Example:
+\begin{prop}
+$ $
+
+Let $\mathcal{R}$ be any R-model:
 
 \begin{itemize}
-Let us show that $\mathcal{Q} \models !A \rightarrow A$.
+  \item $\mathcal{R} \models !A \rightarrow !!A$;
+  \item $\mathcal{R} \models !A \rightarrow A$.
+\end{itemize}
 
-Let $\mathcal{Q} \models !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
+\end{prop}
+
+\begin{proof}
+$ $
+
+\begin{enumerate}
+\item Let us show that $\mathcal{Q} \Vdash !A \rightarrow A$.
+
+Let $\mathcal{Q} \Vdash !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
 Hence there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
-such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$,
-but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \models A$.
+such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$,
+but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \Vdash A$.
 
@@
 
-Let $\langle a, b \rangle \models !A$. Let us show that $\langle a, b \rangle \models !!A$.
+Let $\langle a, b \rangle \Vdash !A$. Let us show that $\langle a, b \rangle \Vdash !!A$.
 
 So there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
-such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$.
+such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$.
 
@@
 so $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models !A$, so  $\langle a, b \rangle \models !!A$.
-\end{itemize}
+\end{enumerate}
+\end{proof}
+
+\begin{theorem} Soundness
+
+  Let $\mathcal{R}$ be a class of $R$-frames, then $Log(\mathcal{R}) = L^{*}_{\bf 1} A_{\bf S 4}$
+\end{theorem}
+
+\begin{proof}
+$ $
+
+Modal cases follows from the previous lemma.
+\end{proof}
 
 \begin{theorem}
+$ $
 
-  Let $\langle A \rangle$
+  Let $W : Fm \to 2^R$, s.t. $W(A) = \{ \langle a, b \rangle \: | \: \mathcal{F}, \langle a, b \rangle \}$, then:
+  \begin{enumerate}
+    \item For each $A \in Fm$, $W(A)$ is a subrelation of $R$;
+    \item
+    \begin{enumerate}
+      \item $W(A \backslash B) = \bigcup \{ \}$
+      \item $W (A / B) = $
+      \item $W (A \circ B) = $
+      \item $W ({\bf 1}) = $
+      \item $W (A \lor B) =$
+      \item $W (A \land B) = $
+    \end{enumerate}
+  \end{enumerate}
+
+\end{theorem}
+
+\begin{defin} Algebra generated by $R$-frame.
+\end{defin}
+
+\begin{theorem}
+$ $
+
+  Any relational quantale is isomorphic to some algebra generated by $R$-frame.
+\end{theorem}
+
+\begin{theorem}
 \end{theorem}
@@
 
-  Let $\mathcal{Q}$ be a relational quantale, then $Log(\mathcal{Q}) = L^{*}(\backslash, /, \bullet, {\bf 1}, \&, \vee)$.
+  If $\Gamma \models_{R} A$, then $L^{*}_{\bf 1} A_{\bf S 4} \vdash \Gamma \rightarrow A$.
+\end{theorem}
+
+\begin{proof}
+\end{proof}
+
+\begin{theorem}
+
 \end{theorem}

### 2019-03-12 PaperDraft.tex
updates

--- 2019-03-08 PaperDraft.tex
@@
 
+\begin{comment}
+
 \begin{defin} Monoidal comonad
@@
 
+\end{comment}
+
 \section{Relational semantics}
@@
 
-Let us define forcing relation $\Vdash$ between elements of $\mathcal{Q}$ and types as follows for arbitrary valuation map $w : Tp \to \mathcal{A}$:
+\begin{theorem}
+  Every unital quantale $\mathcal{Q} = \langle A, \leq, \cdot, \bigvee \rangle$ with quantic conucleus $\Box$ is
+  isomorphic to some relation quantale $\hat{\Box}$
+\end{theorem}
+
+\begin{proof}
+  Consider a relational quantale by Brown and Gurr $\hat{\mathcal{Q}} = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ where:
   \begin{enumerate}
-  \item Let $p_i \in Tp$, then $\langle a, b \rangle \Vdash p_i \Leftrightarrow \langle a, b \rangle \in w(p_i)$;
-  \item $\langle a, b \rangle \Vdash {\bf 1} \Leftrightarrow \langle a, b \rangle \in \mathcal{I}$;
-  \item $\langle a, b \rangle \Vdash A \backslash B \Leftrightarrow \forall c \in A, \langle c, a \rangle \Vdash A \Rightarrow \langle c, b \rangle \Vdash A$;
-  \item $\langle a, b \rangle \Vdash B / A \Leftrightarrow \forall c \in A, \langle a, c \rangle \Vdash A \Rightarrow \langle b, c \rangle \Vdash A$;
-  \item $\langle a, b \rangle \Vdash A \bullet B \Leftrightarrow \exists c, \langle a, c \rangle \Vdash A \text{ and } \langle c, b \rangle \Vdash B$;
-  \item $\langle a, b \rangle \Vdash A \lor B \Leftrightarrow \langle a, b \rangle \Vdash A \text{ or } \langle a, b \rangle \Vdash B$;
-  \item $\langle a, b \rangle \Vdash A \& B \Leftrightarrow \langle a, b \rangle \Vdash A \text{ and } \langle a, b \rangle \Vdash B$;
-  \item $\langle a, b \rangle \Vdash !A \Leftrightarrow \exists S_{\langle a, b \rangle} \forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$
-  \item $\langle a, b \rangle \Vdash \Gamma \rightarrow A \Leftrightarrow \langle a,b \rangle \Vdash A_1 \bullet \dots \bullet A_n \Rightarrow  \langle a,b \rangle \vdash A$;
+    \item $\hat{a} = \{ \langle b, c \rangle \: | \: b \cdot a \leq c \}$;
+    \item $\widehat{a \cdot b} = \hat{a} \circ \hat{b}$;
+    \item $\widehat{\bigvee a} = \bigvee \hat{a}$.
   \end{enumerate}
 
-Example:
+  Consider $\hat{\Box} \hat{a} = \bigvee $
 
-\begin{itemize}
-Let us show that $\mathcal{Q} \models !A \rightarrow A$.
+  \begin{enumerate}
+    \item $\hat{\Box} \hat{a} \subseteq \hat{a}$;
+    \item $\hat{\Box} \hat{a} \subseteq \hat{\Box} \hat{\Box} \hat{a}$;
+    \item $\hat{a} \subseteq \hat{b} \Rightarrow \hat{\Box}\hat{a} \subseteq \hat{\Box}\hat{b}$;
+    \item $\hat{\Box}\hat{a} \circ \hat{\Box}\hat{b} \subseteq \Box(\hat{a} \circ \hat{b})$;
+    \item $\hat{\Box}\hat{\varepsilon} = \hat{\varepsilon}$.
+  \end{enumerate}
 
-Let $\mathcal{Q} \models !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
-Hence there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
-such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$,
-but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \models A$.
+  Let us show that $\hat{\Box} \hat {a} = \widehat{\Box a} = \{ \langle b, c \rangle \: | \:  b \cdot \Box a \leq c \}$
+\end{proof}
 
-\item Let us show that $\mathcal{Q} \models !A \rightarrow !!A$.
+\begin{defin}
+  Let $W$ be a set. A Kripke frame is a pair $\mathcal{W} = \langle W, R, I \rangle$,
+  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.
 
-Let $\langle a, b \rangle \models !A$. Let us show that $\langle a, b \rangle \models !!A$.
+  A Kripke model is a triple $\mathcal{M} = \langle \mathcal{W}, v \rangle$, where
+  $\mathcal{W}$ is a Kripke frame and $v : Tp \to 2^W$.
 
-So there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
-such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$.
+  A forcing relation is defined as follows:
 
-Let $S' \subseteq S_{\langle a, b \rangle}$, then for each $\langle a', b' \rangle \in S', \langle a', b' \rangle \Vdash A$,
-so $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models !A$, so  $\langle a, b \rangle \models !!A$.
-\end{itemize}
+  \begin{enumerate}
+    \item $\mathcal{W}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
+    \item $\mathcal{W}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
+    \item $\mathcal{W}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{W}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{W}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{W}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{W}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
+    \item $\mathcal{W}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
+  \end{enumerate}
+\end{defin}
 
-\begin{theorem}
+\begin{theorem} Soundness
+$ $
 
-  Let $\langle A \rangle$
+  Let $\mathbb{F}$ be a class of Kripke frames, then $Log(\mathbb{F}) = L^{*}_{\bf 1} \land \lor$.
 \end{theorem}
 
-\begin{theorem}
+\begin{proof}
 $ $
 
-  Let $\mathcal{Q}$ be a relational quantale, then $Log(\mathcal{Q}) = L^{*}(\backslash, /, \bullet, {\bf 1}, \&, \vee)$.
+  \begin{enumerate}
+  \item Let $\Gamma \rightarrow A$. By IH, for each $\mathcal{W}, w \Vdash \Gamma \rightarrow A$.
+  \item Let $\Gamma, A, \Delta \rightarrow C$ and $\Gamma, B, \Delta \rightarrow C$,
+  \item Let $\Gamma \rightarrow A$ and $\Gamma \rightarrow B$
+  \item Let $\Gamma \rightarrow A_1 \land A_2$, so $\mathcal{W}, w \Vdash \Gamma \rightarrow A_i$, $i = 1,2$.
+  \end{enumerate}
+\end{proof}
+
+\begin{theorem} Strong completeness
+$ $
+
+  $\Gamma \models A$ implies that $L^{*}_{\bf 1} \land \lor \vdash \Gamma \rightarrow A$
 \end{theorem}
 
+\begin{defin}
+  By ${L^{*}_{\bf 1} \land \lor}_{\bf S4}$ we mean $SMALC_{\Sigma}$, where $\Sigma = \{ s \}$ and $C = W = E = \emptyset$.
+\end{defin}
+
 \end{document}

### 2019-03-13 PaperDraft.tex
update

@@
 \begin{defin}
-  Let $W$ be a set. A Kripke frame is a pair $\mathcal{W} = \langle W, R, I \rangle$,
+  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I \rangle$,
   where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.
@@
   \begin{enumerate}
-    \item $\mathcal{W}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
-    \item $\mathcal{W}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
-    \item $\mathcal{W}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{W}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{W}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{W}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{W}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
-    \item $\mathcal{W}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
+    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
+    \item $\mathcal{M}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
+    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
+    \item $\mathcal{M}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
   \end{enumerate}
@@
 
+\begin{proof}
+\end{proof}
+
+\begin{defin}
+  Mininal normal modal Lambek calculus is $L^{*}_{\bf 1} \land \lor$ with additional rule:
+
+  \begin{prooftree}
+    \AxiomC{$\Gamma \rightarrow A$}
+    \UnaryInfC{$!\Gamma \rightarrow !A$}
+  \end{prooftree}
+\end{defin}
+
 \begin{defin}
@@
 
+\begin{defin}
+  A modal Kripke frame is a 4-tuple $\mathcal{W}_{!} = \langle W, R, Q, I \rangle$, where $Q$ is a preorder on $W$,
+  a Kripke model is tuple $\mathcal{M} \langle \mathcal{W}_{!}, v \rangle$. A forcing relation for $!$ is defined as follows:
+  \item $\mathcal{M}, w \Vdash !A \Leftrightarrow \forall v, Q(w, v) \Rightarrow \mathcal{W}, v \Vdash A$;
+\end{defin}
+
+\begin{theorem} Soundness
+  $ $
+
+  Let $\mathbb{F}$ be a class of modal Kripke frames, then $Log(\mathbb{F}) = {L^{*}_{\bf 1} \land \lor}_{\bf S4}$.
+\end{theorem}
+
+\begin{proof}
+  $ $
+
+  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
+\end{proof}
+
 \end{document}

### 2019-03-15 PaperDraft.tex
representation theorem

@@
 \end{minipage}
+\end{defin}
+
+\begin{defin}
+  By ${L^{*}_{\bf 1} \land \lor}_{\bf S4}$ we mean $SMALC_{\Sigma}$, where $\Sigma = \{ s \}$ and $C = W = E = \emptyset$.
 \end{defin}
@@
 
+\begin{prop}
+  $ $
+
+Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and
+$\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of $\mathcal{Q}_2$.
+
+Then, if $f : \mathcal{Q}_1 \to \mathcal{Q}_2$ is a quantale homomorphism, then $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a subquantale of $\mathcal{Q}_2$.
+\end{prop}
+
+\begin{proof}
+  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$.
+
+  Let $a \in S$, so $\bigvee a \in S$, but $f(a) \in f(\mathcal{S})$, so $f(\bigvee a) = \bigvee (f (a)) \in f(\mathcal{S})$,
+  so $f(\mathcal{S})$ is closed under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
+\end{proof}
+
 \begin{theorem}
-  Every unital quantale $\mathcal{Q} = \langle A, \leq, \cdot, \bigvee \rangle$ with quantic conucleus $\Box$ is
-  isomorphic to some relation quantale $\hat{\Box}$
+  $ $
+
+  Let $\mathcal{Q} = \langle A, \leq, \cdot, \bigvee \rangle$ be a unital quantale and $\mathcal{S}$ is a subquantale of $\mathcal{Q}$.
+
+  Then $\langle \mathcal{Q}, \Box_{\mathcal{S}} \rangle$ is isomorphic to some relational quantale of $A$
+  wit some quantic conucleus $\hat{\Box}$.
 \end{theorem}
@@
 \begin{proof}
-  Consider a relational quantale by Brown and Gurr $\hat{\mathcal{Q}} = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ where:
+  Consider a relational quantale proposed by Brown and Gurr. This quantale is 4-tuple $\theta(\mathcal{Q}) = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ defined as follows:
   \begin{enumerate}
-    \item $\hat{a} = \{ \langle b, c \rangle \: | \: b \cdot a \leq c \}$;
-    \item $\widehat{a \cdot b} = \hat{a} \circ \hat{b}$;
-    \item $\widehat{\bigvee a} = \bigvee \hat{a}$.
+    \item $\theta(a) = \{ \langle b, c \rangle \: | \: b \leq a \cdot c \}$;
+    \item $\theta(a \cdot b) = \theta(a) \circ \theta(b)$;
+    \item $\theta(\bigvee a) = \bigvee \theta(a)$;
+    \item $\theta(\varepsilon) = \{ \langle b, c \rangle \: | \: b \cdot \varepsilon \leq c \} = \{ \langle b, c \rangle \: | \: b \leq c \}$
   \end{enumerate}
 
-  Consider $\hat{\Box} \hat{a} = \bigvee $
+  Let $\mathcal{S} \subseteq \mathcal{Q}$, we define $\Box a = \{ s \: | \: s \in S, s \leq a \}$ is quantic conucleus.
+
+  So, $\theta(S) \subseteq \theta(\mathcal{Q})$ is a subquantale of $\theta(\mathcal{Q})$.
+
+  Let us define $\theta(\Box) \theta{a} := \bigvee \{ \theta{s} \: | \: \theta{s} \in \theta{S}, \theta{s} \subseteq \theta{a} \}$, so
+
+  $\begin{array}{lll}
+  &\theta(\Box a) = \{ \langle p, q \rangle \: | \: p \leq \Box a \cdot q \} = &\\
+  &\{ \langle p, q \rangle \: | \: p \leq \bigvee \{ s \: | \: s \in S, s \leq a \} \cdot q \} = &\\
+  &\theta(\bigvee_{s \in S, s \leq a} s) = & \\
+  &\bigvee_{s \in S, s \leq a} \theta(s) = & \\
+  &\bigvee \{ \theta(s) \: | \: s \in S, s \leq a \} = & \\
+  &\bigvee \{ \theta(s) \: | \: \theta(s) \in \theta(S), \theta(s) \subseteq \theta(a) \} = \theta(\Box) \theta(a)& \\
+  \end{array}$
+
+\end{proof}
+
+\begin{theorem}
+  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
+\end{theorem}
+
+\begin{defin}
+  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I\rangle$,
+  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$ with additional requirements:
 
 \begin{enumerate}
-    \item $\hat{\Box} \hat{a} \subseteq \hat{a}$;
-    \item $\hat{\Box} \hat{a} \subseteq \hat{\Box} \hat{\Box} \hat{a}$;
-    \item $\hat{a} \subseteq \hat{b} \Rightarrow \hat{\Box}\hat{a} \subseteq \hat{\Box}\hat{b}$;
-    \item $\hat{\Box}\hat{a} \circ \hat{\Box}\hat{b} \subseteq \Box(\hat{a} \circ \hat{b})$;
-    \item $\hat{\Box}\hat{\varepsilon} = \hat{\varepsilon}$.
+    \item $R^2 a (b c) d \Leftrightarrow R^2 (a b) c d$;
+    \item $I(b) \Leftrightarrow R a b a \& R b a a$;
+    \item $a \leq b \Leftrightarrow I(c) \& R c a b$;
+    \item $ $
 \end{enumerate}
-
-  Let us show that $\hat{\Box} \hat {a} = \widehat{\Box a} = \{ \langle b, c \rangle \: | \:  b \cdot \Box a \leq c \}$
-\end{proof}
+\end{defin}
 
 \begin{defin}
-  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I \rangle$,
-  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$.
-
   A Kripke model is a triple $\mathcal{M} = \langle \mathcal{W}, v \rangle$, where
@@
     \item $\mathcal{M}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
-    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R(u,v,w) \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R(u,w,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R(w,u,v) \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \forall u, v \in W, R(u,v,w) \text{ either } \mathcal{W}, u \Vdash A \text{ or } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R u v w \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R u w v \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R w u v \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
+    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \exists u, v \in W, S w u v \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
     \item $\mathcal{M}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
@@
 \begin{defin}
-  Mininal normal modal Lambek calculus is $L^{*}_{\bf 1} \land \lor$ with additional rule:
+  Mininal normal modal Lambek calculus ($L{\bf K}$) is $L^{*}_{\bf 1} \land \lor$ with additional rule:
 
@@
   \end{prooftree}
-\end{defin}
-
-\begin{defin}
-  By ${L^{*}_{\bf 1} \land \lor}_{\bf S4}$ we mean $SMALC_{\Sigma}$, where $\Sigma = \{ s \}$ and $C = W = E = \emptyset$.
 \end{defin}

### 2019-03-16 PaperDraft.tex
updates

@@
 
-\begin{defin}
-  Let $W$ be a set. A Kripke frame is a 3-tuple $\mathcal{W} = \langle W, R, I\rangle$,
-  where $R$ is a ternary relation on $W$ and $I$ is an unary relation on $W$ with additional requirements:
-
-\begin{enumerate}
-    \item $R^2 a (b c) d \Leftrightarrow R^2 (a b) c d$;
-    \item $I(b) \Leftrightarrow R a b a \& R b a a$;
-    \item $a \leq b \Leftrightarrow I(c) \& R c a b$;
-    \item $ $
-\end{enumerate}
-\end{defin}
-
-\begin{defin}
-  A Kripke model is a triple $\mathcal{M} = \langle \mathcal{W}, v \rangle$, where
-  $\mathcal{W}$ is a Kripke frame and $v : Tp \to 2^W$.
-
-  A forcing relation is defined as follows:
-
-  \begin{enumerate}
-    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
-    \item $\mathcal{M}, w \Vdash {\bf 1} \Leftrightarrow I(w)$;
-    \item $\mathcal{M}, w \Vdash A \bullet B \Leftrightarrow \exists u, v \in W, R u v w \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash A \backslash B \Leftrightarrow \forall u, v \in W, R u w v \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash B / A \Leftrightarrow \forall u, v \in W, R w u v \text{ and } \mathcal{W}, u \Vdash A \text{ implies } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash A \lor B \Leftrightarrow \exists u, v \in W, S w u v \text{ and } \mathcal{W}, u \Vdash A \text{ and } \mathcal{W}, v \Vdash B$;
-    \item $\mathcal{M}, w \Vdash A \land B \Leftrightarrow \mathcal{W}, w \Vdash A \text{ and } \mathcal{W}, w \Vdash A$;
-    \item $\mathcal{M}, w \Vdash \Gamma \rightarrow A \Leftrightarrow \mathcal{W}, w \Vdash \bullet \Gamma \text{ implies } \mathcal{W}, w \Vdash A$.
-  \end{enumerate}
-\end{defin}
-
-\begin{theorem} Soundness
-$ $
-
-  Let $\mathbb{F}$ be a class of Kripke frames, then $Log(\mathbb{F}) = L^{*}_{\bf 1} \land \lor$.
-\end{theorem}
-
-\begin{proof}
-$ $
-
-  \begin{enumerate}
-  \item Let $\Gamma \rightarrow A$. By IH, for each $\mathcal{W}, w \Vdash \Gamma \rightarrow A$.
-  \item Let $\Gamma, A, \Delta \rightarrow C$ and $\Gamma, B, \Delta \rightarrow C$,
-  \item Let $\Gamma \rightarrow A$ and $\Gamma \rightarrow B$
-  \item Let $\Gamma \rightarrow A_1 \land A_2$, so $\mathcal{W}, w \Vdash \Gamma \rightarrow A_i$, $i = 1,2$.
-  \end{enumerate}
-\end{proof}
-
-\begin{theorem} Strong completeness
-$ $
-
-  $\Gamma \models A$ implies that $L^{*}_{\bf 1} \land \lor \vdash \Gamma \rightarrow A$
-\end{theorem}
-
-\begin{proof}
-\end{proof}
-
-\begin{defin}
-  Mininal normal modal Lambek calculus ($L{\bf K}$) is $L^{*}_{\bf 1} \land \lor$ with additional rule:
-
-  \begin{prooftree}
-    \AxiomC{$\Gamma \rightarrow A$}
-    \UnaryInfC{$!\Gamma \rightarrow !A$}
-  \end{prooftree}
-\end{defin}
-
-\begin{defin}
-  A modal Kripke frame is a 4-tuple $\mathcal{W}_{!} = \langle W, R, Q, I \rangle$, where $Q$ is a preorder on $W$,
-  a Kripke model is tuple $\mathcal{M} \langle \mathcal{W}_{!}, v \rangle$. A forcing relation for $!$ is defined as follows:
-  \item $\mathcal{M}, w \Vdash !A \Leftrightarrow \forall v, Q(w, v) \Rightarrow \mathcal{W}, v \Vdash A$;
-\end{defin}
-
-\begin{theorem} Soundness
-  $ $
-
-  Let $\mathbb{F}$ be a class of modal Kripke frames, then $Log(\mathbb{F}) = {L^{*}_{\bf 1} \land \lor}_{\bf S4}$.
-\end{theorem}
-
-\begin{proof}
-  $ $
-
-  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
-\end{proof}
-
 \end{document}

### 2019-03-16 PaperDraft.tex
updates in notation

@@
 
-  $\Sigma = \langle I, \preceq, W, C, E \rangle$,
+  $\Sigma = \langle \mathcal{I}, \preceq, \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$,
 \end{defin}
 
-where $I = \{ s_1, \dots, s_n\}$, $\langle I, \preceq \rangle$ is a preorder.
-$W, C, E$ are upwardly closed subsets of $I$ and $W \cap C \subseteq E$.
+where $I = \{ s_1, \dots, s_n\}$, $\mathcal{I}, \preceq \rangle$ is a preorder.
+$W, C, E$ are upwardly closed subsets of $I$ and $\mathcal{W} \cap \mathcal{C} \subseteq \mathcal{E}$.
 
@@
 
-  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | !_s \mathcal{F}_{\Sigma} $
+  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | {!_s \mathcal{F}_{\Sigma}}_{s \in \mathcal{I}} $
 \end{defin}
@@
 
-  A quantale is a triple $\langle A, \bigvee, \cdot \rangle$, such that $\langle A, \bigvee \rangle$
-is a complete lattice and $\langle A, \cdot \rangle$ is a semigroup. A quanlate is called unital, if $\langle A, \cdot \rangle$
-is a monoid.
+  A quantale is a triple $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$, such that $\langle A, \bigvee \rangle$
+is a complete lattice and $\langle A, \cdot \rangle$ is a semigroup, such that for all indexing set $I$:
+
+\begin{enumerate}
+  \item $a \cdot \bigvee \limits_{i \in I} b_i = \bigvee \limits_{i \in I} (a \cdot b_i)$;
+  \item $\bigvee \limits_{i \in I} a_i \cdot b = \bigvee \limits_{i \in I} (a_i \cdot b)$
+\end{enumerate}
+
+A quanlate is called unital, if $\langle A, \cdot \rangle$ is a monoid.
 \end{defin}
@@
 \begin{defin}
+
+  Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales. A quantale homomorphism is a map $f : \mathcal{Q}_1 \to \mathcal{Q}_2$, such that:
+
+  \begin{enumerate}
+    \item for all $a,b \in \mathcal{Q}_1$, $f(a \cdot b) = f(a) \cdot f(b)$;
+    \item for all indexing set $I$, $f(\bigvee \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} f(a_i)$.
+  \end{enumerate}
+
+  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism if a quantale homomorphism, such that $f(\varepsilon) = \varepsilon$.
+\end{defin}
+
+\begin{defin}
 $ $
 
-  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale. The center of a quantale is the set $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
+  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale. $\mathcal{S} \subseteq \mathcal{Q}$ is said to be a subquantale, if
+  $\mathcal{S}$ is closed under multiplication and sups.
 \end{defin}
 
-\begin{defin} An open modality (or quantic conucleus) on quantale $\mathcal{Q}$ is a map $\Box : \mathcal{Q} \to \mathcal{Q}$, such that
+There occurs the following simple statement:
+
+\begin{prop}
+  $ $
+
+Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and $\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of $\mathcal{Q}_2$.
+
+Then, if $f : \mathcal{Q}_1 \to \mathcal{Q}_2$ is a quantale homomorphism, then $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a subquantale of $\mathcal{Q}_2$.
+
+In other words, a homomorphic image of subquantale is a subquantale.
+\end{prop}
+
+\begin{proof}
+  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$.
+
+  Let $a_i \in S$ for each $i \in I$, so $\bigvee \limits_{i \in I} a_i \in S$, but $f(a_i) \in f(\mathcal{S})$ for any $i \in I$,
+  so $f(\bigvee \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} (f (a)) \in f(\mathcal{S})$, so $f(\mathcal{S})$ is closed under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
+\end{proof}
+
+\begin{defin}
+$ $
+
+  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale.
+  The center of a quantale is the subquantale $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
+\end{defin}
+
+\begin{defin}
+$ $
+
+  An open modality (or quantic conucleus) on quantale $\mathcal{Q}$ is a map $\Box : \mathcal{Q} \to \mathcal{Q}$, such that
 
@@
 \end{enumerate}
-\end{defin}
 
 For unital quantale, we require that $\Box e = e$.
+\end{defin}
 
@@
 \begin{defin}
+$ $
+
   We define a partial order on open modalities on $\mathcal{Q}$ as $\Box_1 \leq \Box_2 \Leftrightarrow \forall a \in Q, \Box_1 (a) \leq \Box_2 (a)$.
@@
 \begin{lemma}
-  Let $\mathcal{Q}$ be a quantale and $\Box_{\mathcal{Q}}$ be a set of all open modalities on $\mathcal{Q}$.
-  Then $\Box_{\mathcal{Q}}$ is a small category.
+  $\Box_1 a_1 \cdot \Box_2 a_2 \leq \Box^{'} (\Box_1 a_1 \cdot \Box_2 a_2)$, where $\Box_i \leq \Box, i = 1,2$.
 \end{lemma}
@@
 \begin{proof}
-  $\langle \Box_{\mathcal{Q}}, \leq \rangle$ form a partial order, so $\langle \Box_{\mathcal{Q}}, \leq \rangle$ is a small category.
+$ $
+
+  $\begin{array}{lll}
+  &\Box_1 a_1 \cdot \Box_2 a_2 \leq & \\
+  &\Box_1 (\Box_1 a_1) \cdot \Box_2 (\Box_2 a_2) \leq & \\
+  &\Box (\Box_1 a_1) \cdot \Box (\Box_2 a_2) \leq & \\
+  &\Box (\Box_1 (a_1) \cdot \Box_2 (a_2))&
+  \end{array}$
 \end{proof}
@@
 \begin{enumerate}
-  \item An open modality is called central, if $\forall a, b \in Q, \Box(a) \cdot b = b \cdot \Box(a)$.
+  \item An open modality is called central, if for all
+  $a, b \in \mathcal{Q}, \Box(a) \cdot b = b \cdot \Box(a)$.
 
-  \item An open modality is called pseudo-idempotent, if $\forall a, b \in Q, \Box(a) \cdot b \leq \Box(a) \cdot b \cdot \Box(a)$ and
-  $b \cdot \Box(a) \leq \Box(a) \cdot b \cdot \Box(a)$.
+  \item An open modality is called weak square-increasing,
+  if for all $a, b \in \mathcal{Q}, \Box a \cdot b \leq \Box a \cdot b \cdot \Box a$ and
+  $b \cdot \Box a \leq \Box a \cdot b \cdot \Box a$.
 
-  \item An open modality is called unital, if $\forall a \in Q, \Box(a) \leq e$.
+  \item An open modality is called unital, if $\forall a \in Q, \Box a \leq e$.
 \end{enumerate}
@@
 \begin{lemma}
+$ $
+
   Let $\Box$ be an open modality on some unital quantale $\mathcal{Q} = \langle A, \bigvee, \cdot, e \rangle$.
@@
   $\begin{array}{lll}
-  & b \cdot \Box(a) \leq & \\
-  & \:\:\:\: \text{Right weak idempotence}& \\
-  &\Box(a) \cdot b \cdot \Box(a) \leq & \\
+  & b \cdot \Box a \leq & \\
+  & \:\:\:\: \text{Right weak square-increase}& \\
+  &\Box a \cdot b \cdot \Box a \leq & \\
   & \:\:\:\: \text{Unitality}& \\
-  & \Box(a) \cdot b \cdot e \leq & \\
+  & \Box a \cdot b \cdot e \leq & \\
   & \:\:\:\: \text{Identity}& \\
-  &\Box(a) \cdot b \leq & \\
-  & \:\:\:\: \text{Left weak idempotence}& \\
-  &\Box(a) \cdot b \cdot \Box(a) \leq & \\
+  &\Box a \cdot b \leq & \\
+  & \:\:\:\: \text{Left weak square-increase}& \\
+  &\Box a \cdot b \cdot \Box a \leq & \\
   & \:\:\:\: \text{Unitality}& \\
-  &e \cdot b \cdot \Box(a) \leq & \\
+  &e \cdot b \cdot \Box a \leq & \\
   & \:\:\:\: \text{Identity}& \\
@@
 
-Hence, $b \cdot \Box(a) = \Box(a) \cdot b$, so $\forall a \in A, \Box(a) \in \mathcal{Z}(\mathcal{Q})$.
+Hence, $b \cdot \Box a = \Box a \cdot b$, so for all $a \in \mathcal Q, \Box a \in \mathcal{Z}(\mathcal{Q})$.
 
@@
 
-  Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale, then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that
-$\Box(a) = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+  Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale,
+  then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that $\Box(a) = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
 \end{prop}
@@
 
-  Let $\mathcal{Q}$ be a quantale and $S_1 \subseteq S_2 \subseteq \mathcal{Q}$.
+  Let $\mathcal{Q}$ be a quantale and $\mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$.
 
-  Then $\Box_1 (a) \leq \Box_2 (a)$.
+  Then $\Box_{\mathcal{S}_1} (a) \leq \Box_{\mathcal{S}_1} (a)$.
 \end{prop}
@@
 
-Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale, then the following operations are open modalities:
+Let $\mathcal{Q}$ be a quantale and $\mathcal{S} \subseteq \mathcal{Q}$ a subquantale, then the following operations are open modalities:
 
@@
   Follows from Lemma 3.
-\end{proof}
-
-\begin{lemma}
-  $\Box_1(a_1) \cdot \Box_2(a_2) \leq \Box^{'} (\Box_1(a_1) \cdot \Box_2(a_2))$, where $\Box_i \leq \Box^{'}, i = 1,2$.
-\end{lemma}
-
-\begin{proof}
-$ $
-
-  $\begin{array}{lll}
-  &\Box_1(a_1) \cdot \Box_2(a_2) \leq & \\
-  &\Box_1 (\Box_1 (a_1)) \cdot \Box_2 (\Box_2 (a_2)) \leq & \\
-  &\Box^{'} (\Box_1 (a_1)) \cdot \Box^{'} (\Box_2 (a_2)) \leq & \\
-  &\Box^{'}(\Box_1 (a_1) \cdot \Box_2 (a_2))&
-  \end{array}$
 \end{proof}
@@
 \begin{lemma}
-  Let $!_s \in I$ and $A$ be an arbitrary formula, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ B \: | \: !_s B \rightarrow A \}$
+  Let $!_s \in I$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$
   is a quantic conucleus.
@@
 \begin{lemma}
-  Let $A$ be a formula, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$.
+  Let $A \in \mathcal{F}_{\Sigma}$, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$.
 \end{lemma}
@@
 
-  Let $i, j \in I$ and $i \preceq j$, then for all $A \in Fm$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
+  Let $i, j \in I$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
 \end{lemma}
@@
 
-  Let $i, j \in I$ and $i \preceq j$. Then forall $A \in Fm$, $!_j A \rightarrow !_i A$ by promotion.
+  Let $i, j \in I$ and $i \preceq j$, then forall $A \in \mathcal{F}_{\Sigma}$, $!_j A \rightarrow !_i A$ by promotion.
   Then $\bigvee \{ !_j A \} \subseteq \bigvee \{ !_i A \}$, so $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
@@
 
+For all $A \in \mathcal{F}_{\Sigma}$,
   \begin{enumerate}
-    \item Let $s \in W$, then for all $A \subseteq Fm$, $\Box_s \{ A \} \subseteq \{ {\bf 1} \}$;
+    \item Let $s \in W$, then $\Box_s \{ A \} \subseteq \{ {\bf 1} \}$;
     \item Let $s \in E$, then $\Box_s (\bigvee \{ A \}) \cdot \bigvee \{ B \} = \bigvee \{ B\} \cdot \Box_s (\bigvee \{ A \})$.
@@
     \item $\langle \mathcal{A}, \circ, \mathcal{I} \rangle$ is a monoid;
-    \item For each indexing set $J$, $R \circ \bigvee_{j \in J} S_j = \bigvee_{j \in J} (R \circ S_j)$ and
-      $\bigvee_{j \in J} R_j \circ S = \bigvee_{j \in J}(R_j \circ S)$.
+    \item For each indexing set $J$, $R \circ \bigvee_{i \in I} S_i = \bigvee_{i \in I} (R \circ S_i)$ and
+      $\bigvee_{i \in I} R_i \circ S = \bigvee_{i \in I}(R_i \circ S)$.
   \end{itemize}
 \end{defin}
-
-\begin{prop}
-  $ $
-
-Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and
-$\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of $\mathcal{Q}_2$.
-
-Then, if $f : \mathcal{Q}_1 \to \mathcal{Q}_2$ is a quantale homomorphism, then $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a subquantale of $\mathcal{Q}_2$.
-\end{prop}
-
-\begin{proof}
-  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$.
-
-  Let $a \in S$, so $\bigvee a \in S$, but $f(a) \in f(\mathcal{S})$, so $f(\bigvee a) = \bigvee (f (a)) \in f(\mathcal{S})$,
-  so $f(\mathcal{S})$ is closed under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
-\end{proof}
 
@@
 \begin{proof}
-  Consider a relational quantale proposed by Brown and Gurr. This quantale is 4-tuple $\theta(\mathcal{Q}) = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ defined as follows:
+$ $
+
+  Consider a relational quantale proposed by Brown and Gurr.
+
+  This quantale is 4-tuple $\theta(\mathcal{Q}) = \langle \mathcal{R}, \subseteq, \circ, \bigvee \rangle$ defined as follows:
   \begin{enumerate}
@@
     \item $\theta(a \cdot b) = \theta(a) \circ \theta(b)$;
-    \item $\theta(\bigvee a) = \bigvee \theta(a)$;
+    \item $\theta(\bigvee \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} \theta(a_i)$;
     \item $\theta(\varepsilon) = \{ \langle b, c \rangle \: | \: b \cdot \varepsilon \leq c \} = \{ \langle b, c \rangle \: | \: b \leq c \}$
@@
 
-  Let $\mathcal{S} \subseteq \mathcal{Q}$, we define $\Box a = \{ s \: | \: s \in S, s \leq a \}$ is quantic conucleus.
+  Let $\mathcal{S} \subseteq \mathcal{Q}$, so $\Box_{\mathcal{S}} a := \bigvee \{ s \: | \: s \in S, s \leq a \}$ is quantic conucleus.
 
@@
 
-  Let us define $\theta(\Box) \theta{a} := \bigvee \{ \theta{s} \: | \: \theta{s} \in \theta{S}, \theta{s} \subseteq \theta{a} \}$, so
+  Let us define $\hat{\Box} \theta(a) := \bigvee \{ \theta(s) \: | \: \theta(s) \in \theta(S), \theta(s) \subseteq \theta(a) \}$, so
 
   $\begin{array}{lll}
-  &\theta(\Box a) = \{ \langle p, q \rangle \: | \: p \leq \Box a \cdot q \} = &\\
-  &\{ \langle p, q \rangle \: | \: p \leq \bigvee \{ s \: | \: s \in S, s \leq a \} \cdot q \} = &\\
+  &\theta(\Box_{\mathcal{S}} a) = \{ \langle p, q \rangle \: | \: p \leq \Box_{\mathcal{S}} a \cdot q \} = &\\
+  &\{ \langle p, q \rangle \: | \: p \leq \bigvee \{ s \: | \: s \in \mathcal{S}, s \leq a \} \cdot q \} = &\\
+  &\:\:\:\: \text{Homomorphism}& \\
   &\theta(\bigvee_{s \in S, s \leq a} s) = & \\
+  &\:\:\:\: \text{Homomorphism preserves sups}& \\
   &\bigvee_{s \in S, s \leq a} \theta(s) = & \\
+  &\:\:\:\: \text{Unfolding}& \\
   &\bigvee \{ \theta(s) \: | \: s \in S, s \leq a \} = & \\
-  &\bigvee \{ \theta(s) \: | \: \theta(s) \in \theta(S), \theta(s) \subseteq \theta(a) \} = \theta(\Box) \theta(a)& \\
+  &\:\:\:\: \text{Unfolding}& \\
+  &\bigvee \{ \theta(s) \: | \: \theta(s) \in \theta(S), \theta(s) \subseteq \theta(a) \} = \hat{\Box} \theta(a)& \\
   \end{array}$
+
+So, $\hat{\Box} \theta(a) = \theta(\Box_{\mathcal{S}} a)$.
 

### 2019-03-19 RModels.tex
add stuff on p-morphisms

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{dsfont}
\usepackage{mathabx}
\usepackage[all, 2cell]{xy}
\usepackage[all]{xy}
\usepackage{wasysym}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{trfsigns}
\usepackage{cmll}
\usepackage{authblk}

\theoremstyle{defin}
\newtheorem{defin}{Definition}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}

\theoremstyle{prop}
\newtheorem{prop}{Proposition}

\theoremstyle{lemma}
\newtheorem{lemma}{Lemma}

\theoremstyle{ex}
\newtheorem{ex}{Example}

\theoremstyle{col}
\newtheorem{col}{Corollary}
\usepackage{listings} 		% for source code
\date{}
\author[1,2]{Daniel Rogozin}
\affil[1]{Lomonosov Moscow State University}
\affil[2]{Serokell O\"{U}}
\title{On $R$-models}

\begin{document}

\maketitle

\begin{defin}
  $ $

  $R$-model is a pair $\mathcal{M} = \langle W, R, v \rangle$,
  where $R$ is a transitive relation on $W$ and $v : Tp \to 2^R$ is a valuation, such that:

  \begin{enumerate}
    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
    \item $\mathcal{M}, \langle a, b \rangle \Vdash A \bullet B \Leftrightarrow
      \text{there exists $c \in W$, $\mathcal{M}, a \Vdash A$ and $\mathcal{M}, b \Vdash B$}$;
    \item $\mathcal{M}, \langle a, b \rangle \Vdash A \backslash B \Leftrightarrow
      \text{for all $c \in R^{-1}(a)$, $\mathcal{M}, \langle c, a \rangle \Vdash A$ implies
      $\mathcal{M}, \langle c, b \rangle \Vdash B$}$;
      \item $\mathcal{M}, \langle a, b \rangle \Vdash B / A \Leftrightarrow
        \text{for all $c \in R(a)$, $\mathcal{M}, \langle a, c \rangle \Vdash A$ implies
        $\mathcal{M}, \langle b, c \rangle \Vdash B$}$;
  \end{enumerate}
\end{defin}

\begin{defin}
  $ $

  Let $\mathcal{F}_1$, $\mathcal{F}_2$ be $R$-frames and
  $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$, $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$
  be $R$-models.

  A map $f : W_1 \to W_2$ is said to be a $R$-frame $p$-morphism if the following conditions hold:

  \begin{enumerate}
    \item $f$ is onto;
    \item $\forall a, b \in W_1 (a R_1 b \Rightarrow f(a) R_2 f (b))$ (monotonicity);
    \item $\forall d \in W_1, c \in W_2, f(d) R_2 c \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: d R_1 c'$ (left lift property);
    \item $\forall d \in W_1, c \in W_2, c R_2 f(d) \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: c' R_1 d$ (right lift property);
  \end{enumerate}

  A map $f : \mathcal{F}_1 \to \mathcal{F}_2$ is $R$-model $p$-moprhism, iff:

  \begin{itemize}
    \item $\mathcal{M}_1, \langle a, b \rangle \Vdash p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash p_i$
  \end{itemize}
\end{defin}

\begin{lemma}
  Let $f : \mathcal{M}_1 \to \mathcal{M}_2$ be a $p$-morphism, then
  $\mathcal{M}_1, \langle a, b \rangle \Vdash A \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A$,
  for all $a, b \in W_1$ and for all $A \in Fm$
\end{lemma}

\begin{proof}
$ $

  \begin{enumerate}
    \item $\Rightarrow$
      \begin{enumerate}
        \item Basic case: follows from the definition.
        \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}_1, \langle a, b \rangle \Vdash B \bullet C$, then
        there exists $c \in W_1$, such that $\mathcal{M}_1, \langle a, c \rangle \Vdash B$ and
        $\mathcal{M}_1, \langle c, b \rangle \Vdash C$.

        Then, $a R_1 c$ and $c R_1 b$, so $f(a) R_2 f(c)$ and $f(c) R_2 f(b)$.

        Thus, by IH, $\mathcal{M}_2, \langle f(a), f(c) \rangle \Vdash B$ and
        $\mathcal{M}_2, \langle f(c), f(b) \rangle \Vdash C$, so $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \bullet C$.
        \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_1, \langle a, b \rangle \Vdash B \backslash C$.
        Let $c \in W_2$, such that $c R_2 f(a)$.

        Then, by left lift property, there exist $d \in W_1$, such that $f(d) = c$ and $d R_1 a$.

        Thus, $\mathcal{M}_1, \langle d, a \rangle \Vdash A$ implies
        $\mathcal{M}_1, \langle d, b \rangle \Vdash B$.

        By IH, $\mathcal{M}_2, \langle c, f(a) \rangle \Vdash A$ implies
        $\mathcal{M}_2, \langle c, f(b) \rangle \Vdash B$, then $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A \backslash B$.

        \item Similarly to (c), but via right lift property.
      \end{enumerate}
    \item $\Leftarrow$
    \begin{enumerate}
      \item Basic case: follows from the definition.

      \item Let $A \eqcirc B \bullet C$.
      Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \bullet C$. Then
      there exists $c \in W_2$, such that $\mathcal{M}_2, \langle f(a), c \rangle \Vdash B$ and
      $\mathcal{M}_2, \langle c, f(b) \rangle \Vdash C$.

      So far as $f$ is surjection, then there exists $d \in W_1$, such that
      $c = f(d)$, then $\mathcal{M}_2, \langle f(a), f(d) \rangle \Vdash B$ and
      $\mathcal{M}_2, \langle f(d), f(b) \rangle \Vdash C$, and, by IH,
      $\mathcal{M}_1, \langle a, d \rangle \Vdash B$ and $\mathcal{M}_1, \langle d, b \rangle \Vdash C$,
      then $\mathcal{M}_1, \langle a, b \rangle \Vdash B \bullet C$.

      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \backslash C$.

      Let $c \in W_1$ and $c R_1 a$, then $f(c) R_1 f(a)$ by monotonicity,
      so $\mathcal{M}_2, \langle f(c), f(a) \rangle \Vdash A$ implies
      $\mathcal{M}_2, \langle f(c), f(b) \rangle \Vdash B$.

      By IH, $\mathcal{M}_1, \langle c, a \rangle \Vdash A$ implies
      $\mathcal{M}_1, \langle c, b \rangle \Vdash B$. Thus, $\mathcal{M}_1, \langle c, a \rangle \Vdash A \backslash B$.
      \item Similarly to (c).
    \end{enumerate}
  \end{enumerate}
\end{proof}

\begin{lemma}
$ $

  \begin{enumerate}
    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.

    Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.

    \item Let $\mathcal{F}_1$ and $\mathcal{F}_2$ be $R$-frames and $\mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$,
    then $\mathcal{F}_1 \models A$ implies $\mathcal{F}_2 \models A$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  Standardly.
\end{proof}

\end{document}

### 2019-03-19 RModels.tex
update p-morphism lemma

@@
         $\mathcal{M}, \langle b, c \rangle \Vdash B$}$;
+    \item $\mathcal{M}, \langle a, b \rangle \Vdash \Gamma \rightarrow A \Leftrightarrow
+    \mathcal{M}, \langle a, b \rangle \Vdash \Gamma \text{ implies } \mathcal{M}, \langle a, b \rangle \Vdash A$
   \end{enumerate}
 \end{defin}
+
+where $\mathcal{M}, \langle a, b \rangle \Vdash \Gamma$ denotes $\mathcal{M}, \langle a, b \rangle \Vdash A_1 \bullet \dots \bullet A_n$, or,
+equivalently, there exist $c_1, \dots, c_{n-1}$,
+such that $\mathcal{M}, \langle a, c_1 \rangle \Vdash A_1,
+\mathcal{M}, \langle c_1, c_2 \rangle \Vdash A_2, \dots,
+\mathcal{M}, \langle c_{n-1}, b \rangle \Vdash A_n$ implies that $\mathcal{M}, \langle a, b \rangle \Vdash B$.
+
+\begin{theorem}
+  Let $\mathbb{F}$ is a $R$-frame, then $\mathbb{F} \models L$.
+\end{theorem}
 
@@
 \begin{lemma}
-  Let $f : \mathcal{M}_1 \to \mathcal{M}_2$ be a $p$-morphism, then
+  Let $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$, then
   $\mathcal{M}_1, \langle a, b \rangle \Vdash A \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A$,
@@
         \item Similarly to (c), but via right lift property.
+        \item Let $\mathcal{M}_1, \langle a, b \rangle \Vdash A_1, \dots, A_n \rightarrow A$.
+
+        Thus, there exist $c_1, \dots, c_{n-1} \in W_1$, such that
+        $\mathcal{M}_1, \langle a, c_1 \rangle \Vdash A_1, \dots, \mathcal{M}_1, \langle c_{n-2}, c_{n-1} \rangle \Vdash A_n$
+        implies that $\mathcal{M}_1, \langle c_{n-1}, b \rangle \Vdash B$.
+
+        By IH, $\mathcal{M}_2, \langle f(a), f(c_1) \rangle \Vdash A_1, \dots, \mathcal{M}_1, \langle f(c_{n-1}), f(b) \rangle \Vdash A_n$.
+
+        So, $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A_1 \bullet \dots \bullet A_n$.
+
+        Thus, $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B$.
       \end{enumerate}
@@
       \item Similarly to (c).
+      \item Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash \Gamma \rightarrow A$, so
+      by case (b) and IH, $\mathcal{M}_2, \langle a, b \rangle \Gamma$, so $\mathcal{M_1}, \langle a, b \rangle A$.
     \end{enumerate}
@@
   \begin{enumerate}
-    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.
-
-    Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.
+    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$. Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.
 
@@
     then $\mathcal{F}_1 \models A$ implies $\mathcal{F}_2 \models A$.
+
+    \item $\mathcal{F}_1 \cong \mathcal{F}_2$, then $Log(\mathcal{F}_1) = Log(\mathcal{F}_2)$.
   \end{enumerate}

### 2019-04-04 RModels.tex
add calculus def
prove p-morphism lemma explicitly

@@
 
+  \begin{prooftree}
+  \AxiomC{$ $}
+  \RightLabel{\scriptsize{ax}}
+  \UnaryInfC{$A \rightarrow A$}
+  \end{prooftree}
+
+\begin{minipage}{0.5\textwidth}
+  \begin{flushleft}
+        \begin{prooftree}
+      \AxiomC{$\Gamma \rightarrow A$}
+      \AxiomC{$\Delta, B, \Theta \rightarrow C$}
+      \RightLabel{$\backslash \rightarrow$}
+      \BinaryInfC{$\Delta, \Gamma, A \backslash B, \Theta \rightarrow C$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma \rightarrow A$}
+      \AxiomC{$\Delta, B, \Theta \rightarrow C$}
+      \RightLabel{$/ \rightarrow$}
+      \BinaryInfC{$\Delta, B / A, \Gamma, \Theta \rightarrow C$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma, A, B, \Delta \rightarrow C$}
+      \RightLabel{$\bullet \rightarrow$}
+      \UnaryInfC{$\Gamma, A \bullet B, \Delta \rightarrow C$}
+    \end{prooftree}
+\end{flushleft}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+  \begin{flushright}
+       \begin{prooftree}
+      \AxiomC{$A, \Pi \rightarrow B$}
+      \RightLabel{$\rightarrow \backslash$}
+      \UnaryInfC{$\Pi \rightarrow A \backslash B$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Pi, A \rightarrow B$}
+      \RightLabel{$\rightarrow /$}
+      \UnaryInfC{$\Pi \rightarrow B / A$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma \rightarrow A$}
+      \AxiomC{$\Delta \rightarrow B$}
+      \RightLabel{$\rightarrow \bullet$}
+      \BinaryInfC{$\Gamma, \Delta \rightarrow A \bullet B$}
+    \end{prooftree}
+\end{flushright}
+\end{minipage}
+\end{defin}
+
+\begin{defin}
+  $ $
+
   $R$-model is a pair $\mathcal{M} = \langle W, R, v \rangle$,
@@
 \begin{theorem}
-  Let $\mathbb{F}$ is a $R$-frame, then $\mathbb{F} \models L$.
+  Let $\mathbb{F}$ be a $R$-frame, then $\mathbb{F} \models L$.
 \end{theorem}
@@
 
-  \begin{itemize}
-    \item $\mathcal{M}_1, \langle a, b \rangle \Vdash p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash p_i$
-  \end{itemize}
+\begin{center}
+ $\mathcal{M}_1, \langle a, b \rangle \Vdash p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash p_i$
+\end{center}
+
 \end{defin}
@@
         \item Similarly to (c), but via right lift property.
-        \item Let $\mathcal{M}_1, \langle a, b \rangle \Vdash A_1, \dots, A_n \rightarrow A$.
-
-        Thus, there exist $c_1, \dots, c_{n-1} \in W_1$, such that
-        $\mathcal{M}_1, \langle a, c_1 \rangle \Vdash A_1, \dots, \mathcal{M}_1, \langle c_{n-2}, c_{n-1} \rangle \Vdash A_n$
-        implies that $\mathcal{M}_1, \langle c_{n-1}, b \rangle \Vdash B$.
-
-        By IH, $\mathcal{M}_2, \langle f(a), f(c_1) \rangle \Vdash A_1, \dots, \mathcal{M}_1, \langle f(c_{n-1}), f(b) \rangle \Vdash A_n$.
-
-        So, $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A_1 \bullet \dots \bullet A_n$.
-
-        Thus, $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B$.
       \end{enumerate}
@@
       \item Similarly to (c).
-      \item Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash \Gamma \rightarrow A$, so
-      by case (b) and IH, $\mathcal{M}_2, \langle a, b \rangle \Gamma$, so $\mathcal{M_1}, \langle a, b \rangle A$.
     \end{enumerate}
@@
   \begin{enumerate}
-    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$. Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.
+    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.
+    Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.
 
-    \item Let $\mathcal{F}_1$ and $\mathcal{F}_2$ be $R$-frames and $\mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$,
+    \item Let $\mathcal{F}_1$ and $\mathcal{F}_2$ be $R$-frames and $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$,
     then $\mathcal{F}_1 \models A$ implies $\mathcal{F}_2 \models A$.
-
-    \item $\mathcal{F}_1 \cong \mathcal{F}_2$, then $Log(\mathcal{F}_1) = Log(\mathcal{F}_2)$.
   \end{enumerate}
@@
 \begin{proof}
-  Standardly.
+$ $
+
+\begin{enumerate}
+  \item
+  \begin{itemize}
+    \item Only if:
+
+    Let $\mathcal{M}_1 \models A$. Let $c, d \in W_2$. So far as $f$ is onto,
+    then there exists $a, b \in W_1$, such that $f(a) = c$ and $f(b) = d$.
+
+    Then $\mathcal{M}_1, \langle a, b \rangle \Vdash A$, thus $\mathcal{M}_2 \langle f(a), f(b) \rangle \Vdash A$.
+    That is, $\mathcal{M}_2 \langle c, d \rangle \Vdash A$
+
+    \item If:
+
+    Follows from the previous lemma.
+  \end{itemize}
+  \item Let $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ and $\mathcal{F}_1 \models A$.
+
+  Let $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$ and $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$, such that
+  for all $p \in Tp$,
+  $\mathcal{M}_1, \langle a, b \rangle \Vdash p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \Vdash p$.
+  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \models A$. Thus, $\mathcal{M}_2 \models A$.
+\end{enumerate}
 \end{proof}

### 2019-04-07 PaperDraft.tex
prove p-morphism lemma explicitly
updates in notation and defs

@@
 \affil[2]{Serokell O\"{U}}
-\title{Models of Lambek calculus enriched with subexponentials}
+\title{Models of Lambek calculus with subexponentials}
 
@@
 
-  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | {!_s \mathcal{F}_{\Sigma}}_{s \in \mathcal{I}} $
+  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash
+  \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | ({!_s \mathcal{F}_{\Sigma}})_{s \in
+  \Sigma} $
 \end{defin}
@@
 
-\begin{defin}
-  By ${L^{*}_{\bf 1} \land \lor}_{\bf S4}$ we mean $SMALC_{\Sigma}$, where $\Sigma = \{ s \}$ and $C = W = E = \emptyset$.
-\end{defin}
-
 \begin{theorem}
@@
 
-Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and $\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of $\mathcal{Q}_2$.
+Let $\mathcal{Q}_1$, $\mathcal{Q}_2$ be quantales and $\mathcal{S} \subseteq \mathcal{Q}_1$ is a subquantale of
+$\mathcal{Q}_1$.
 
@@
 \begin{proof}
-  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$.
+$ $
 
-  Let $a_i \in S$ for each $i \in I$, so $\bigvee \limits_{i \in I} a_i \in S$, but $f(a_i) \in f(\mathcal{S})$ for any $i \in I$,
-  so $f(\bigvee \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} (f (a)) \in f(\mathcal{S})$, so $f(\mathcal{S})$ is closed under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
+  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$. Let $a_i \in S$ for each $i
+  \in I$, so $\bigvee \limits_{i \in I} a_i \in S$, but $f(a_i) \in f(\mathcal{S})$ for any $i \in I$, so $f(\bigvee
+  \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} (f (a)) \in f(\mathcal{S})$, so $f(\mathcal{S})$ is closed
+  under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
 \end{proof}
@@
 \begin{lemma}
-  $\Box_1 a_1 \cdot \Box_2 a_2 \leq \Box^{'} (\Box_1 a_1 \cdot \Box_2 a_2)$, where $\Box_i \leq \Box, i = 1,2$.
+  $\Box_1 a_1 \cdot \Box_2 a_2 \leq \Box (\Box_1 a_1 \cdot \Box_2 a_2)$, where $\Box_i \leq \Box, i = 1,2$.
 \end{lemma}
@@
   \item An open modality is called central, if for all
-  $a, b \in \mathcal{Q}, \Box(a) \cdot b = b \cdot \Box(a)$.
+  $a, b \in \mathcal{Q}, \Box a \cdot b = b \cdot \Box a$.
 
@@
   & \:\:\:\: \text{Identity}& \\
-  &b \cdot \Box(a)&
+  &b \cdot \Box a&
   \end{array}$
@@
   Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale,
-  then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that $\Box(a) = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+  then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
 \end{prop}
@@
 \begin{proof}
-  See
+  See Rosenthal.
 \end{proof}
@@
   \item $\Box_{idem} (a) = \bigvee \{ s \in S \: | s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$;
-  \item $\Box_{z, \mathds{1}}, I_{z, idem}, I_{\mathds{1}, idem}, I_{z, \mathds{1}, idem}$.
+  \item Operations with combinations of conditions above;
 \end{enumerate}
@@
 
-\begin{prop}
-  $\bigvee S$ is an ideal.
-\end{prop}
+The following conditions hold similarly to \cite{Gurr}:
 
 \begin{lemma}
-  $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$.
+$ $
+
+  \begin{enumerate}
+  \item $\bigvee S$ is an ideal;
+  \item $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$;
+  \item $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$;
+  \item Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
+  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
+  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a unital quantale.
+  \end{enumerate}
 \end{lemma}
 
-\begin{proof}
-$ $
-
-Let $A \in Fm$. Then $\{ B \: | \: B \rightarrow A', A' \in A \} \subseteq \bigvee \{ A \}$,
-so far as $\bigvee A$ is an ideal.
-
-On the other hand, $\{ B \: | \: B \rightarrow A \}$ is an ideal, it is easy to see that this set is closed under $\lor$.
-So, $\bigvee A \subseteq \{ B \: | \: B \rightarrow A \}$.
-\end{proof}
-
-\begin{lemma}
-  $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$.
-\end{lemma}
-
-\begin{proof}
-  Let $\bigvee \{ A \} \subseteq \bigvee \{ B \}$,
-  then $\{ C | C \rightarrow A \} \subseteq \{ D \: | \: D \rightarrow B \}$.
-
-Thus, $A \in \{ C | C \rightarrow A \}$,
-then $A \in \{ D \: | \: D \rightarrow B \}$, hence $A \rightarrow B$.
-
-On the other hand, let $A \rightarrow B$ and $C \in \bigvee \{ A \}$.
-
-Thus, $C \rightarrow A$, then $C \rightarrow B$ by cut.
-
-\end{proof}
-
-\begin{lemma}
-  Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
-  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
-  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a quantale.
-\end{lemma}
-
-\begin{proof}
-  See
-\end{proof}
+We extend this construction for polymodal case as follows:
 
@@
 
+\begin{enumerate}
   \item Follows from $!_s A \rightarrow {\bf 1}$, so $s \in W$;
@@
   \item Follows from $!_s A \bullet B \rightarrow !_s A \bullet B \bullet !_s A$ and similarly for $B \bullet !_s A$.
+\end{enumerate}
 \end{proof}
@@
 
-Let $Q$ be a syntactic quantale as proposed above and
+Let $\mathcal{Q}$ be a syntactic quantale as proposed above and
 $\mathcal{I} = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature.
@@
 
-  Let $Q$ be a quantale constructed above and $\Box_1, \dots, \Box_n$ be a family of quantic conuclei on $Q$.
+  Let $Q$ be a quantale constructed above and $(\Box_{s_i})_{s_i \in \Sigma}$ be a family of quantic conuclei on $Q$.
   Then there exist a model $\langle Q, [\![.]\!]\rangle$, such that $[\![A]\!] = \bigvee \{ A \}$, $A \in Fm$.
@@
 
-  Let $A$ be a set. Then relational quantale on $A$ is a tuple $\mathcal{Q} = \langle \mathcal{A}, \mathcal{I} \rangle$
-  where $\mathcal{A} \subseteq 2^{A \times A}$:
+  Let $A$ be a set. Then relational quantale on $A$ is a triple $\mathcal{Q} = \langle \mathcal{A}, \bigvee, \mathcal{I}
+  \rangle$ where $\mathcal{A} \subseteq 2^{A \times A}$:
 
   \begin{itemize}
-    \item $\langle \mathcal{A}, \subseteq \rangle$ is a complete semi-lattice;
+    \item $\langle \mathcal{A}, \bigvee, \subseteq \rangle$ is a complete semi-lattice;
     \item Multiplication is defined as
@@
 
-\begin{theorem}
-  $\Gamma \models A$, then ${L^{*}_{\bf 1} \land \lor}_{\bf S4} \vdash \Gamma \rightarrow A$
-\end{theorem}
+\section{Syntactic concept lattices}
+
+\begin{defin}
+  Let $\mathcal{L}$ be a finite alphabet and $L \subseteq \mathcal{L}^{*}$ be a language.
+
+  We define maps $[.]^{\triangleright} : \mathcal{P}(\mathcal{L}^{*}) \to \mathcal{P}(\mathcal{L}^{*} \times \mathcal{L}^{*})$
+  and $[.]^{\triangleleft} : \mathcal{P}(\mathcal{L}^{*} \times \mathcal{L}^{*}) \to \mathcal{P}(\mathcal{L}^{*})$ as follows:
+
+  \begin{enumerate}
+    \item $M \subseteq \mathcal{L}^{*}$, $M^{\triangleright} = \{ (x, y) \: | \: \forall w \in M, x w y \in L \}$;
+    \item $C \subseteq \mathcal{L}^{*} \times \mathcal{L}^{*}$, $C^{\triangleleft} = \{ w \: | \: \forall (x, y) \in C, x w y
+    \in L\}$
+  \end{enumerate}
+\end{defin}
+
+Note that compositions $[.]^{\triangleleft \triangleright}$ and $[.]^{\triangleright \triangleleft}$ form closure operators,
+by the way $[.]^{\triangleleft}$ and $[.]^{\triangleright}$ are connected via contravariant Galois connection.
+
+\begin{defin} A syntactic concept is a pair $\langle S, C \rangle$, where $S \subseteq \mathcal{L}^{*}$
+  and $C \subseteq \mathcal{L}^{*} \times \mathcal{L}^{*}$, such that $S^{\triangleright} = C$ and $C^{\triangleleft} = S$.
+\end{defin}
 

### 2019-04-07 RModels.tex
updates in notation and defs

@@
 \begin{theorem}
-  Let $\mathbb{F}$ be a $R$-frame, then $\mathbb{F} \models L$.
+  Let $\mathbb{F}$ be a $R$-frame, then $\mathbb{F} \Vdash L$.
 \end{theorem}
@@
     \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.
-    Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.
+    Then $\mathcal{M}_1 \Vdash A$ iff $\mathcal{M}_2 \Vdash A$.
 
     \item Let $\mathcal{F}_1$ and $\mathcal{F}_2$ be $R$-frames and $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$,
-    then $\mathcal{F}_1 \models A$ implies $\mathcal{F}_2 \models A$.
+    then $\mathcal{F}_1 \Vdash A$ implies $\mathcal{F}_2 \Vdash A$.
   \end{enumerate}
@@
 
-    Let $\mathcal{M}_1 \models A$. Let $c, d \in W_2$. So far as $f$ is onto,
+    Let $\mathcal{M}_1 \Vdash A$. Let $c, d \in W_2$. So far as $f$ is onto,
     then there exists $a, b \in W_1$, such that $f(a) = c$ and $f(b) = d$.
@@
   \end{itemize}
-  \item Let $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ and $\mathcal{F}_1 \models A$.
+  \item Let $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ and $\mathcal{F}_1 \Vdash A$.
 
@@
   $\mathcal{M}_1, \langle a, b \rangle \Vdash p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \Vdash p$.
-  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \models A$. Thus, $\mathcal{M}_2 \models A$.
+  Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \Vdash A$. Thus, $\mathcal{M}_2 \Vdash A$.
 \end{enumerate}
@@
 
+\begin{defin}
+\end{defin}
+
 \end{document}

### 2019-04-22 PaperDraft.tex
updates in drafts and proofs

@@
   Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale.
-  The center of a quantale is the subquantale $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
+  The centre of a quantale is the subquantale $\mathcal{Z}(\mathcal{Q}) = \{ a \in A \: | \: \forall b \in A, a \cdot b = b \cdot a \}$
 \end{defin}
@@
 
+Following to Wurm, by the concept we mean a closed set of strings, that is, $A$ is a concept iff $A \triangleright
+\triangleleft = A$. Moreover, $\langle \mathcal{B}_{\mathcal{L}}, \bigvee, \bigwedge \rangle$, where
+$\mathcal{B}_{\mathcal{L}}$ is the set of $\triangleright \triangleleft$-closed subsets of $\mathcal{L}^{*}$.
+
+We define a product of concepts as $A \circ B = (A \cdot B)^{\triangleright \triangleleft} =
+\{ a b \: | \: a \in A, b \in B \}^{\triangleright \triangleleft}$.
+
+Residuals are defined explicitly as follows:
+
+\begin{center}
+  $A \backslash B = \{ (a B, b) \: | \: (a, b) \in A^{\triangleright} \}^{\triangleleft}$
+
+  $B / A = \{ (a, B b) \: | \: (a, b) \in A^{\triangleright} \}^{\triangleleft}$
+\end{center}
+
+It is easy to see, that the following condition hold for that residuals:
+
+\begin{center}
+  $A \backslash B = \{ C \: | \: A \circ C \leq B \}$
+
+  $B / A = \bigvee \{ C \: | \: C \circ A \leq B \}$
+\end{center}
+
+\begin{defin}
+  The syntax concept lattice of a language $L$ is a structure $\langle \mathcal{B}_{L}, \circ, \bigvee, \bigwedge, /,
+  \backslash \rangle$, where $\mathcal{B}_{L}$ is the set of $[.]^{\triangleright \triangleleft}$-closed subsets of
+  $\mathcal{L}^{*}$.
+\end{defin}
+
+\section{Thanks}
+
+Author would like to thank Lev Beklemishev, Stepan Kuznetsov, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov
+for advice, critics, and comments.
+
 \end{document}

### 2019-04-22 RModels.tex
updates in drafts and proofs

--- 2019-04-04 RModels.tex
@@
   \begin{enumerate}
-    \item $\mathcal{M}, w \Vdash p_i \Leftrightarrow w \in v(p_i)$;
-    \item $\mathcal{M}, \langle a, b \rangle \Vdash A \bullet B \Leftrightarrow
-      \text{there exists $c \in W$, $\mathcal{M}, a \Vdash A$ and $\mathcal{M}, b \Vdash B$}$;
-    \item $\mathcal{M}, \langle a, b \rangle \Vdash A \backslash B \Leftrightarrow
-      \text{for all $c \in R^{-1}(a)$, $\mathcal{M}, \langle c, a \rangle \Vdash A$ implies
-      $\mathcal{M}, \langle c, b \rangle \Vdash B$}$;
-    \item $\mathcal{M}, \langle a, b \rangle \Vdash B / A \Leftrightarrow
-        \text{for all $c \in R(a)$, $\mathcal{M}, \langle a, c \rangle \Vdash A$ implies
-        $\mathcal{M}, \langle b, c \rangle \Vdash B$}$;
-    \item $\mathcal{M}, \langle a, b \rangle \Vdash \Gamma \rightarrow A \Leftrightarrow
-    \mathcal{M}, \langle a, b \rangle \Vdash \Gamma \text{ implies } \mathcal{M}, \langle a, b \rangle \Vdash A$
+    \item $\mathcal{M}, w \models p_i \Leftrightarrow w \in v(p_i)$;
+    \item $\mathcal{M}, \langle a, b \rangle \models A \bullet B \Leftrightarrow
+      \text{there exists $c \in W$, $\mathcal{M}, a \models A$ and $\mathcal{M}, b \models B$}$;
+    \item $\mathcal{M}, \langle a, b \rangle \models A \backslash B \Leftrightarrow
+      \text{for all $c \in R^{-1}(a)$, $\mathcal{M}, \langle c, a \rangle \models A$ implies
+      $\mathcal{M}, \langle c, b \rangle \models B$}$;
+    \item $\mathcal{M}, \langle a, b \rangle \models B / A \Leftrightarrow
+        \text{for all $c \in R(a)$, $\mathcal{M}, \langle a, c \rangle \models A$ implies
+        $\mathcal{M}, \langle b, c \rangle \models B$}$;
+    \item $\mathcal{M}, \langle a, b \rangle \models \Gamma \rightarrow A \Leftrightarrow
+    \mathcal{M}, \langle a, b \rangle \models \Gamma \text{ implies } \mathcal{M}, \langle a, b \rangle \models A$
   \end{enumerate}
@@
 
-where $\mathcal{M}, \langle a, b \rangle \Vdash \Gamma$ denotes $\mathcal{M}, \langle a, b \rangle \Vdash A_1 \bullet \dots \bullet A_n$, or,
-equivalently, there exist $c_1, \dots, c_{n-1}$,
-such that $\mathcal{M}, \langle a, c_1 \rangle \Vdash A_1,
-\mathcal{M}, \langle c_1, c_2 \rangle \Vdash A_2, \dots,
-\mathcal{M}, \langle c_{n-1}, b \rangle \Vdash A_n$ implies that $\mathcal{M}, \langle a, b \rangle \Vdash B$.
+where $\mathcal{M}, \langle a, b \rangle \models \Gamma$ denotes $\mathcal{M}, \langle a, b \rangle \models A_1 \bullet \dots \bullet A_n$, or,
+equivalently, there exist $c_1, \dots, c_{n-1}$, such that $\mathcal{M}, \langle a, c_1 \rangle \models A_1,
+\mathcal{M}, \langle c_1, c_2 \rangle \models A_2, \dots, \mathcal{M}, \langle c_{n-1}, b \rangle \models A_n$ implies that
+$\mathcal{M}, \langle a, b \rangle \models B$.
 
@@
 
-  Let $\mathcal{F}_1$, $\mathcal{F}_2$ be $R$-frames and
-  $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$, $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$
+  Let $\mathcal{F}_1$, $\mathcal{F}_2$ be $R$-frames and $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$, $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$
   be $R$-models.
@@
     \item $\forall d \in W_1, c \in W_2, f(d) R_2 c \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: d R_1 c'$ (left lift property);
-    \item $\forall d \in W_1, c \in W_2, c R_2 f(d) \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: c' R_1 d$ (right lift property);
+    \item $\forall d \in W_1, c \in W_2, c R_2 f(d) \Rightarrow \exists c' \in W_1, f(c') = c \: \& \: c' R_1 d$ (right lift property).
   \end{enumerate}
@@
 \begin{center}
- $\mathcal{M}_1, \langle a, b \rangle \Vdash p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash p_i$
+ $\mathcal{M}_1, \langle a, b \rangle \models p_i \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \models p_i$
 \end{center}
@@
   Let $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$, then
-  $\mathcal{M}_1, \langle a, b \rangle \Vdash A \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A$,
+  $\mathcal{M}_1, \langle a, b \rangle \models A \Leftrightarrow \mathcal{M}_2, \langle f(a), f(b) \rangle \models A$,
   for all $a, b \in W_1$ and for all $A \in Fm$
@@
         \item Basic case: follows from the definition.
-        \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}_1, \langle a, b \rangle \Vdash B \bullet C$, then
-        there exists $c \in W_1$, such that $\mathcal{M}_1, \langle a, c \rangle \Vdash B$ and
-        $\mathcal{M}_1, \langle c, b \rangle \Vdash C$.
+        \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}_1, \langle a, b \rangle \models B \bullet C$, then
+        there exists $c \in W_1$, such that $\mathcal{M}_1, \langle a, c \rangle \models B$ and
+        $\mathcal{M}_1, \langle c, b \rangle \models C$.
 
@@
 
-        Thus, by IH, $\mathcal{M}_2, \langle f(a), f(c) \rangle \Vdash B$ and
-        $\mathcal{M}_2, \langle f(c), f(b) \rangle \Vdash C$, so $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \bullet C$.
-        \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_1, \langle a, b \rangle \Vdash B \backslash C$.
+        Thus, by IH, $\mathcal{M}_2, \langle f(a), f(c) \rangle \models B$ and
+        $\mathcal{M}_2, \langle f(c), f(b) \rangle \models C$, so $\mathcal{M}_2, \langle f(a), f(b) \rangle \models B \bullet C$.
+        \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_1, \langle a, b \rangle \models B \backslash C$.
         Let $c \in W_2$, such that $c R_2 f(a)$.
@@
 
-        Thus, $\mathcal{M}_1, \langle d, a \rangle \Vdash A$ implies
-        $\mathcal{M}_1, \langle d, b \rangle \Vdash B$.
+        Thus, $\mathcal{M}_1, \langle d, a \rangle \models A$ implies
+        $\mathcal{M}_1, \langle d, b \rangle \models B$.
 
-        By IH, $\mathcal{M}_2, \langle c, f(a) \rangle \Vdash A$ implies
-        $\mathcal{M}_2, \langle c, f(b) \rangle \Vdash B$, then $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash A \backslash B$.
+        By IH, $\mathcal{M}_2, \langle c, f(a) \rangle \models A$ implies
+        $\mathcal{M}_2, \langle c, f(b) \rangle \models B$, then $\mathcal{M}_2, \langle f(a), f(b) \rangle \models A \backslash B$.
 
@@
       \item Let $A \eqcirc B \bullet C$.
-      Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \bullet C$. Then
-      there exists $c \in W_2$, such that $\mathcal{M}_2, \langle f(a), c \rangle \Vdash B$ and
-      $\mathcal{M}_2, \langle c, f(b) \rangle \Vdash C$.
+      Let $\mathcal{M}_2, \langle f(a), f(b) \rangle \models B \bullet C$. Then
+      there exists $c \in W_2$, such that $\mathcal{M}_2, \langle f(a), c \rangle \models B$ and
+      $\mathcal{M}_2, \langle c, f(b) \rangle \models C$.
 
-      So far as $f$ is surjection, then there exists $d \in W_1$, such that
-      $c = f(d)$, then $\mathcal{M}_2, \langle f(a), f(d) \rangle \Vdash B$ and
-      $\mathcal{M}_2, \langle f(d), f(b) \rangle \Vdash C$, and, by IH,
-      $\mathcal{M}_1, \langle a, d \rangle \Vdash B$ and $\mathcal{M}_1, \langle d, b \rangle \Vdash C$,
-      then $\mathcal{M}_1, \langle a, b \rangle \Vdash B \bullet C$.
+      So far as $f$ is onto, then there exists $d \in W_1$, such that $c = f(d)$, then $\mathcal{M}_2, \langle f(a), f(d) \rangle \models B$ and
+      $\mathcal{M}_2, \langle f(d), f(b) \rangle \models C$, and, by IH, $\mathcal{M}_1, \langle a, d \rangle \models B$ and
+      $\mathcal{M}_1, \langle d, b \rangle \models C$, then $\mathcal{M}_1, \langle a, b \rangle \models B \bullet C$.
 
-      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_2, \langle f(a), f(b) \rangle \Vdash B \backslash C$.
+      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}_2, \langle f(a), f(b) \rangle \models B \backslash C$.
 
-      Let $c \in W_1$ and $c R_1 a$, then $f(c) R_1 f(a)$ by monotonicity,
-      so $\mathcal{M}_2, \langle f(c), f(a) \rangle \Vdash A$ implies
-      $\mathcal{M}_2, \langle f(c), f(b) \rangle \Vdash B$.
+      Let $c \in W_1$ and $c R_1 a$, then $f(c) R_1 f(a)$ by monotonicity, so $\mathcal{M}_2, \langle f(c), f(a) \rangle \models A$ implies
+      $\mathcal{M}_2, \langle f(c), f(b) \rangle \models B$.
 
-      By IH, $\mathcal{M}_1, \langle c, a \rangle \Vdash A$ implies
-      $\mathcal{M}_1, \langle c, b \rangle \Vdash B$. Thus, $\mathcal{M}_1, \langle c, a \rangle \Vdash A \backslash B$.
+      By IH, $\mathcal{M}_1, \langle c, a \rangle \models A$ implies $\mathcal{M}_1, \langle c, b \rangle \models B$. Thus,
+      $\mathcal{M}_1, \langle c, a \rangle \models A \backslash B$.
       \item Similarly to (c).
@@
   \begin{enumerate}
-    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$.
-    Then $\mathcal{M}_1 \models A$ iff $\mathcal{M}_2 \models A$.
+    \item Let $\mathcal{M}_1$ and $\mathcal{M}_2$ be $R$-models and $f : \mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$. Then $\mathcal{M}_1 \models A$ iff
+    $\mathcal{M}_2 \models A$.
 
@@
 
-    Let $\mathcal{M}_1 \models A$. Let $c, d \in W_2$. So far as $f$ is onto,
-    then there exists $a, b \in W_1$, such that $f(a) = c$ and $f(b) = d$.
+    Let $\mathcal{M}_1 \models A$. Let $c, d \in W_2$. So far as $f$ is onto, then there exists $a, b \in W_1$, such that $f(a) = c$ and $f(b) = d$.
 
-    Then $\mathcal{M}_1, \langle a, b \rangle \Vdash A$, thus $\mathcal{M}_2 \langle f(a), f(b) \rangle \Vdash A$.
-    That is, $\mathcal{M}_2 \langle c, d \rangle \Vdash A$
+    Then $\mathcal{M}_1, \langle a, b \rangle \models A$, thus $\mathcal{M}_2 \langle f(a), f(b) \rangle \models A$.
+    That is, $\mathcal{M}_2 \langle c, d \rangle \models A$
 
@@
   Let $\mathcal{M}_1 = \langle \mathcal{F}_1, v_1 \rangle$ and $\mathcal{M}_2 = \langle \mathcal{F}_2, v_2 \rangle$, such that
-  for all $p \in Tp$,
-  $\mathcal{M}_1, \langle a, b \rangle \Vdash p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \Vdash p$.
+  for all $p \in Tp$, $\mathcal{M}_1, \langle a, b \rangle \models p \Leftrightarrow_{def} \mathcal{M}_1, \langle f(a), f(b) \rangle \models p$.
   Thus, $\mathcal{M}_1 \twoheadrightarrow \mathcal{M}_2$ and $\mathcal{M}_1 \models A$. Thus, $\mathcal{M}_2 \models A$.
@@
 
+\begin{defin}
+  $ $
+
+\begin{enumerate}
+  \item Let $\mathcal{F} = \langle W, R \rangle$ be a transitive frame and $V \subseteq W$, such that $V \neq \emptyset$ and $V$ is
+  downward and upward closed with respect to $R$. Then a frame $\mathcal{F} \restriction V = \langle V, R \cap V \times V \rangle$ is a generated subframe.
+  \item If, $\mathcal{M} = \langle W, R, \theta$ and $V \subseteq W$, such that $\mathcal{F} \restriction V$ is a genereted subframe. Then
+  $\mathcal{M} \restriction V = \langle V, R \cap V \times V, \theta^{'}\rangle$ is a generated submodel, where $\theta^{'}(p) = \theta(p) \cap V$.
+\end{enumerate}
+\end{defin}
+
+\begin{lemma}
+  Let $\mathcal{M} = \langle W, R, \theta$ and $V$ is $R$-closed subset of $W$, then:
+  \begin{enumerate}
+    \item If $a, b \in V$, then $\mathcal{M}, \langle a, b \rangle \models A$ iff $\mathcal{M} \restriction V, \langle a, b \rangle \models A$;
+    \item $Log(\mathcal{F}) \subseteq Log(\mathcal{F} \restriction V)$
+  \end{enumerate}
+\end{lemma}
+
+\begin{proof}
+  $ $
+  \begin{enumerate}
+    \item
+    \begin{enumerate}
+      \item Let $a, b \in V$ and $\langle a, b \rangle \in \theta(p)$, then $\mathcal{M} \restriction V, \langle a, b \rangle \models p$, for $p \in Tp$.
+      \item Let $A \eqcirc B \bullet C$ and $\mathcal{M}, \langle a, b \rangle \models B \bullet C$, then
+      there exists $c \in W$, such that $a R C$ and $\mathcal{M}, \langle a, c \rangle \models B$, $c R b$ and $\mathcal{M}, \langle c, b \rangle \models C$.
+      So far as $V$ is upwardly and downwardly closed, then $c \in V$. Then, by IH, $\mathcal{M} \restriction V , \langle a, c \rangle \models B$, $c R b$ and
+      $\mathcal{M} \restriction V, \langle c, b \rangle \models C$. So $\mathcal{M} \restriction V \langle a, b \rangle \models B \bullet C$.
+      \item Let $A \eqcirc B \backslash C$ and $\mathcal{M}, \langle a, b \rangle \models B \backslash C$. Then for all $c \in R^{-1}(a)$, $\mathcal{M},
+      \langle c, a \rangle \models B$ implies $\mathcal{M}, \langle c, b \rangle \models C$. Let $\mathcal{M}, \langle c, a \rangle \models B$.
+      By IH, $\mathcal{M} \restriction V, \langle c, a \rangle \models B$.
+
+      $c \in V$, because $V$ is $R$-closed upwardly and downloadly. On the other hand, $c R b$, so $b \in V$. Hence,
+      $\langle c, b \rangle \in \mathcal{F} \restriction V$. By IH, $\mathcal{M} \restriction V, \langle c, b \rangle \models C$. Hence,
+      $\mathcal{M} \restriction V, \langle a, b \rangle \models A \backslash B$.
+    \end{enumerate}
+    \item Let $\mathcal{F} \restriction V\not\models \Gamma \to A$. Then there exist a valuation $v$ and $\langle a, b \rangle \in R \cap V \times V$,
+    such that $\mathcal{M} \restriction V, \langle a,b \rangle \models \Gamma$ and $\mathcal{M} \restriction V, \langle a,b \rangle\not\models A$.
+
+    Let us define a valuation $v^{'}$ for the frame $\mathcal{F}$, such that $v(p) = v^{'}(p)$.
+Then, by the first part, $\mathcal{M}, \langle a, b \rangle \models \Gamma$ and $\mathcal{M}, \langle a, b\rangle\not\models A$.
+So, $\mathcal{F}\not\models \Gamma \to A$.
+  \end{enumerate}
+\end{proof}
+
+\begin{col}
+  $ $
+
+  Let $\mathcal{F}$ be a frame and $\mathcal{F} \restriction V$ is a generated subframe of $\mathcal{F}$.
+  Then $Log(\mathcal{F}) = Log(\mathcal{F} \restriction V)$.
+\end{col}
+
+Let $\mathbb{Z}^{*}$ be the set of all finite sequences of integers. Let us define the following relation $R$.
+
 \end{document}

### 2019-06-03 PaperDraft.tex
representation theorem

@@
 \date{}
-\author[1,2]{Daniel Rogozin}
+\author[1,2]{Danya Rogozin}
 \affil[1]{Lomonosov Moscow State University}
@@
 
-So, $\hat{\Box} \theta(a) = \theta(\Box_{\mathcal{S}} a)$.
+Thus, $\hat{\Box} \theta(a) = \theta(\Box_{\mathcal{S}} a)$.
 
+\end{proof}
+
+\begin{theorem}
+  Let $\mathfrak{Q} = \langle \mathcal{Q}, I \rangle$ be a quantale with
+  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some quantic conucleus.
+\end{theorem}
+
+\begin{proof}
+  Let $I$ be a quantic conucleus. Then $\mathcal{Q}_{I} = \{ a \in \mathcal{Q} \: | \: I(a) = a \}$ is a subquantale of $\mathcal{Q}$.
+
+  Let us define $I'(a) = \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \}$.
+
+  It is clear that $I'$ is a quantic conucleus. Let us show that for all
+  $a \in \mathcal{Q}$ $I(a) = I'(a)$.
+
+  $\begin{array}{lll}
+  & I'(a) = \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = & \\
+  & \bigvee \{ s \in \mathcal{Q}_{I} \: | \: I(s) \leq a \} = & \\
+  & \bigvee \{ s \in \mathcal{Q}_{I} \: | \: I(s) \leq I(a) \} \leq I(a)&
+  \end{array}$
+
+  It is clear that, $I(a) \leq a$. So $I(a) \leq \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = I'(a)$.
+
+  Thus, we showed that $I(a) = I'(a)$. One need to apply the previous theorem with $I'$.
 \end{proof}
@@
 \begin{center}
-  $A \backslash B = \{ C \: | \: A \circ C \leq B \}$
+  $A \backslash B = \bigvee \{ C \: | \: A \circ C \leq B \}$
 
@@
 Author would like to thank Lev Beklemishev, Stepan Kuznetsov, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov
-for advice, critics, and comments.
+for advice, critique, and comments.
 

### 2019-06-16 PaperDraft.tex
updates in the draft

@@
 
-\section{The Lambek Calculus with subexponentials}
-
-\begin{defin} A subexponential signature is an ordered quintuple:
-
-  $\Sigma = \langle \mathcal{I}, \preceq, \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$,
-\end{defin}
-
-where $I = \{ s_1, \dots, s_n\}$, $\mathcal{I}, \preceq \rangle$ is a preorder.
-$W, C, E$ are upwardly closed subsets of $I$ and $\mathcal{W} \cap \mathcal{C} \subseteq \mathcal{E}$.
-
-\begin{defin}
-$ $
-
-  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash
-  \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | ({!_s \mathcal{F}_{\Sigma}})_{s \in
-  \Sigma} $
-\end{defin}
-
-\begin{defin} Noncommutative linear logic with subexponentials ($SMALC_{\Sigma}$), where $\Sigma$ is a subexponential signature.
+\section{Introduction}
+
+Categorial grammars were initially introduced by Ajdukiewicz and Bar-Hillel \cite{Ajd} \cite{Bar}.
+In the 1950s, Lambek proposed the way of proof-theoretical consideration of such grammars \cite{Lambek}.
+In this approach, language is logic and parsing is derivation via inference rules.
+Let us consider a quite simple example.
+One needs to parse this quote from the poem by Oscar Wilde called "Impression du Matin" \cite{Wilde}:
+
+\begin{center}
+The Thames nocture of blue and gold \\
+Changed to Harmony in grey
+\end{center}
+
+The first is to assign the correpsonding syntactic caterogies to the words as follows:
+
+\vspace{\baselineskip}
+
+$ $ \:\:\:\: The \:\:\:\: Thames nocturne \:\:\:\:\:\: of \:\:\:\:\:\:\:\:\:\: blue \:\:\:\:\:\:\: and \:\:\:\:\:\:\:\: gold
+
+$(np / n) / np$ \:\:\:\:\: $np$ \:\:\:\:\:\:\:\:\: $n$ \:\:\:\:\:\: $np \backslash (np / ad)$ \: $ad$ \:\: $ad / (ad \backslash ad)$ \: $ad$
+
+\vspace{\baselineskip}
+
+$ $ \: Changed \:\:\:\: to \:\:\:\: Harmony \:\:\:\:\:\:\:\:\:\: in \:\:\:\:\:\:\:\:\:\:\: grey
+
+$ $ \: $np \backslash (s / p)$ \:\: $p / np$ \:\:\:\:\:\: $np$ \:\:\:\:\:\:\:\: $np \backslash (np / ad)$ \:\: $ad$ \:\:\:\:\:\: $\rightarrow s$
+
+\vspace{\baselineskip}
+
+Here the basic reduction rules are:
+
+\begin{itemize}
+  \item $A, A \backslash B \to B$
+  \item $B / A, A \to B$
+\end{itemize}
+
+Here we assign the special syntactic categories to the words of this sentence.
+$np$ denotes "noun phrase", $n$ -- noun, $ad$ -- adjective, $p$ -- phrase, $s$ -- sentence.
+This sequent denotes that this Oscar Wilde's quote is a well-formed sentence.
+The verb "changed" has type "$np$ under ($s$ over $p$)". In other words, one needs to apply some noun phrase ("The Thames
+nocturne of blue and gold") from the left, apply some phrase from the right ("Changed to Harmony in grey") and obtain
+sentence after that. The other syntactic categories might be considered similarly.
+
+The general case of such derivations in categorial grammars is axiomatised via Lambek calculus \cite{Lambek}, non-commutative
+linear logic.
 
@@
   \end{prooftree}
-
+\end{flushleft}
+\end{minipage}\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{flushright}
+  \begin{prooftree}
+    \AxiomC{$A, \Pi \rightarrow B$}
+    \RightLabel{$\rightarrow \backslash, \Pi \text{ is non-empty}$}
+    \UnaryInfC{$\Pi \rightarrow A \backslash B$}
+  \end{prooftree}
+
+  \begin{prooftree}
+    \AxiomC{$\Pi, A \rightarrow B$}
+    \RightLabel{$\rightarrow /, \Pi \text{ is non-empty}$}
+    \UnaryInfC{$\Pi \rightarrow B / A$}
+  \end{prooftree}
+
+  \begin{prooftree}
+    \AxiomC{$\Gamma \rightarrow A$}
+    \AxiomC{$\Delta \rightarrow B$}
+    \RightLabel{$\rightarrow \bullet$}
+    \BinaryInfC{$\Gamma, \Delta \rightarrow A \bullet B$}
+  \end{prooftree}
+\end{flushright}
+\end{minipage}
+
+\begin{prooftree}
+  \AxiomC{$\Gamma \rightarrow A$}
+  \AxiomC{$\Pi, A, \Delta \rightarrow B$}
+  \RightLabel{${\bf cut}$}
+  \BinaryInfC{$\Gamma, \Pi, \Delta \rightarrow B$}
+\end{prooftree}
+
+Note that, non-commutativity is no coincidence. We cannot assume that a sentence remains well-formed regardless
+of the word order.
+
+As you could see, non-commutativity yields two implications: the left one (or, left division) and the right one (or, right division).
+Moreover, the right introduction rules for these divisions have the special restriction that claims non-emptiness
+of the sequence $\Pi$ in the antecedent. This restriction denotes that we have no empty word that makes no sense
+linguistically. On the other hand, we can avoid this restriction. This calculus is called $L^{*}$. Note that, the empty word
+might be introduced explicilty via the constant ${\bf 1}$. The logic $L_{\bf 1}$ is a conservative extension of $L^{*}$ with
+the following inference rules:
+
+\begin{minipage}{0.5\textwidth}
+\begin{flushleft}
+
+  \begin{prooftree}
+    \AxiomC{$\Gamma, \Delta \rightarrow A$}
+    \RightLabel{${\bf 1} \rightarrow$}
+    \UnaryInfC{$\Gamma, {\bf 1}, \Delta \rightarrow A$}
+  \end{prooftree}
+
+  \end{flushleft}
+\end{minipage}\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{flushright}
+
+  \begin{prooftree}
+    \AxiomC{$ $}
+    \RightLabel{$\rightarrow {\bf 1}$}
+    \UnaryInfC{$\rightarrow {\bf 1}$}
+  \end{prooftree}
+
+\end{flushright}
+\end{minipage}
+
+Also, we have a multiplicative conjunction or non-commutative tensor. This connective plays the role of concatenation.
+
+One may extend Lambek calculus with so-called additive conjunction and disjunction. The inference rules for these connections
+are quite similar to inference rules for conjunction and disjunction in intuitionistic sequent calculus. In $L$-models,
+additive connections are intersection and union of languages:
+
+\begin{minipage}{0.5\textwidth}
+\begin{flushleft}
     \begin{prooftree}
       \AxiomC{$\Gamma, A_i, \Delta \rightarrow B$}
-      \RightLabel{$\&, i = 1,2 \rightarrow$}
-      \UnaryInfC{$\Gamma, A_1 \& A_2, \Delta \rightarrow B$}
+      \RightLabel{$\land \rightarrow, i = 1,2$}
+      \UnaryInfC{$\Gamma, A_1 \land A_2, \Delta \rightarrow B$}
     \end{prooftree}
@@
     \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Gamma, \Delta \rightarrow A$}
-      \RightLabel{${\bf 1} \rightarrow$}
-      \UnaryInfC{$\Gamma, {\bf 1}, \Delta \rightarrow A$}
-    \end{prooftree}
-
+  \end{flushleft}
+\end{minipage}\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{flushright}
+  \begin{prooftree}
+    \AxiomC{$\Gamma \rightarrow A$}
+    \AxiomC{$\Gamma \rightarrow B$}
+    \RightLabel{$\rightarrow \land$}
+    \BinaryInfC{$\Gamma \rightarrow A \land B$}
+  \end{prooftree}
+
+  \begin{prooftree}
+    \AxiomC{$\Gamma \rightarrow A_i$}
+    \RightLabel{$\rightarrow \vee, i = 1,2$}
+    \UnaryInfC{$\Gamma \rightarrow A_1 \vee A_2$}
+  \end{prooftree}
+\end{flushright}
+\end{minipage}
+
+\section{The Lambek Calculus with subexponentials}
+
+Let us consider the following phrase as an example.
+
+\begin{center}
+  The young lady whom Childe Harold met before his pilgrimage
+\end{center}
+
+There is "the young lady" in the middle of this phrase. We are incapable of processing such cases in the core Lambek
+calculus. That is, there is no ability to extract from the middle. "Met" is a phrasal verb. Whom did Childe Halord meet? He
+met the young lady.
+
+  \vspace{\baselineskip}
+
+\begin{center}
+The young lady whom$_i$ Childe Harold met $e_i$ before his pilgrimage
+\end{center}
+
+  \vspace{\baselineskip}
+
+For this purpose, we introduce the exponential modality with exchange rule. The left one rule is a
+dereliction, which is similar to the left $\Box$ introduction in modal logic $T$.
+
+  \vspace{\baselineskip}
+
+\begin{minipage}{0.5\textwidth}
+\begin{flushleft}
+  \begin{prooftree}
+    \AxiomC{$\Gamma, A, \Delta \rightarrow B$}
+    \RightLabel{$(! \to)$}
+    \UnaryInfC{$\Gamma, ! A, \Delta \rightarrow B$}
+  \end{prooftree}
+\end{flushleft}
+\end{minipage}\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{flushright}
+  \begin{prooftree}
+    \AxiomC{$\Gamma, ! A, \Delta, \Theta \rightarrow C$}
+    \RightLabel{${\bf ex}$}
+    \UnaryInfC{$\Gamma, \Delta, ! A, \Theta \rightarrow C$}
+  \end{prooftree}
+\end{flushright}
+\end{minipage}
+
+  \vspace{\baselineskip}
+
+The another one phrase is related to so-called parasitic extraction:
+
+\begin{center}
+The letter that Young Werther sent to Charlotte without reading
+\end{center}
+
+In addition to medial extraction, we used "the letter" twice in this phrase. Thus, one need to multiply our linguistical resources in a restricted way.
+
+\begin{center}
+The letter that$_i$ Young Werther sent $e_i$ to Charlotte without reading $e_i$
+\end{center}
+
+Subexponential modality with non-local contraction allows one to do such operations:
+
+  \vspace{\baselineskip}
+
+\begin{minipage}{0.5\textwidth}
+\begin{flushleft}
+  \begin{prooftree}
+    \AxiomC{$\Gamma, ! A, \Delta, ! A, \Theta \rightarrow B$}
+    \RightLabel{${\bf contr}$}
+    \UnaryInfC{$\Gamma, \Delta, ! A, \Theta \rightarrow B$}
+  \end{prooftree}
+\end{flushleft}
+\end{minipage}\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{flushright}
+  \begin{prooftree}
+    \AxiomC{$\Gamma, ! A, \Delta, ! A, \Theta \rightarrow B$}
+    \RightLabel{${\bf contr}$}
+    \UnaryInfC{$\Gamma, ! A, \Delta, \Theta \rightarrow B$}
+  \end{prooftree}
+\end{flushright}
+\end{minipage}
+
+  \vspace{\baselineskip}
+
+Note that, the usual form of contraction yields the cut inadmissibility in contrast to non-local contraction, which generalises the contraction.
+
+  \vspace{\baselineskip}
+
+It is useful to have many modalities and distinguish them in accordance with their abilities. In other words, we are going to
+consider the polymodal case. Let us introduce a subexponential signature, which is a preorder with upwardly closed subsets,
+where $W$ denotes weakening, etc. Note that, a subexponential signature might have any cardinality you prefer: finite or
+infinite.
+
+\begin{defin} A subexponential signature is an ordered quintuple:
+
+  $\Sigma = \langle \mathcal{I}, \preceq, \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$,
+where $\langle \mathcal{I}, \preceq \rangle$ is a preorder.
+$\mathcal{W}, \mathcal{C}, \mathcal{E}$ are upwardly closed subsets of $I$ and $\mathcal{W} \cap \mathcal{C} \subseteq \mathcal{E}$.
+\end{defin}
+
+The last condition claims that if there are weakening and contraction, then one may also exchange as follows.
+
+\begin{prooftree}
+  \AxiomC{$\Gamma, ! A, \Delta, \Theta \rightarrow B$}
+  \RightLabel{${\bf weak}$}
+  \UnaryInfC{$\Gamma, ! A, \Delta, ! A, \Theta \rightarrow B$}
+  \RightLabel{${\bf ncontr}$}
+  \UnaryInfC{$\Gamma, \Delta, ! A, \Theta \rightarrow B$}
+\end{prooftree}
+
+\begin{defin}
+$ $
+
+  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash
+  \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | ({!_s \mathcal{F}_{\Sigma}})_{s \in
+  \Sigma} $
+\end{defin}
+
+\begin{defin} Noncommutative linear logic with subexponentials ($SMALC_{\Sigma}$), where $\Sigma$ is a subexponential signature.
+
+    \vspace{\baselineskip}
+
+\begin{minipage}{0.5\textwidth}
+  \begin{flushleft}
     \begin{prooftree}
@@
     \end{prooftree}
+
+    \begin{prooftree}
+    \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
+    \RightLabel{${\bf ncontr}_1, s \in C$}
+    \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
+    \end{prooftree}
+
+    \begin{prooftree}
+    \AxiomC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
+    \RightLabel{${\bf ex}_1, s \in E$}
+    \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow A$}
+    \end{prooftree}
+
   \end{flushleft}
@@
   \begin{flushright}
-    \begin{prooftree}
-      \AxiomC{$A, \Pi \rightarrow B$}
-      \RightLabel{$\rightarrow \backslash$}
-      \UnaryInfC{$\Pi \rightarrow A \backslash B$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Pi, A \rightarrow B$}
-      \RightLabel{$\rightarrow /$}
-      \UnaryInfC{$\Pi \rightarrow B / A$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Gamma \rightarrow A$}
-      \AxiomC{$\Delta \rightarrow B$}
-      \RightLabel{$\rightarrow \bullet$}
-      \BinaryInfC{$\Gamma, \Delta \rightarrow A \bullet B$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Gamma \rightarrow A$}
-      \AxiomC{$\Gamma \rightarrow B$}
-      \RightLabel{$\rightarrow \&$}
-      \BinaryInfC{$\Gamma \rightarrow A \& B$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Gamma \rightarrow A_i$}
-      \RightLabel{$\rightarrow \vee, i = 1,2$}
-      \UnaryInfC{$\Gamma \rightarrow A_1 \vee A_2$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$ $}
-      \RightLabel{$\rightarrow {\bf 1}$}
-      \UnaryInfC{$\rightarrow {\bf 1}$}
-    \end{prooftree}
-
     \begin{prooftree}
@@
     \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
+      \RightLabel{${\bf ncontr}_2, s \in C$}
+      \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
+      \RightLabel{${\bf ex}_2, s \in E$}
+      \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow A$}
+    \end{prooftree}
   \end{flushright}
 \end{minipage}
-Structural rules:
-
-\begin{minipage}{0.5\textwidth}
-  \begin{flushleft}
-        \begin{prooftree}
-        \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
-        \RightLabel{${\bf ncontr}_1, s \in C$}
-        \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
-        \end{prooftree}
-
-        \begin{prooftree}
-        \AxiomC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
-        \RightLabel{${\bf ex}_1, s \in E$}
-        \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow A$}
-        \end{prooftree}
 
@@
 
-  \end{flushleft}
-\end{minipage}
-\begin{minipage}{0.5\textwidth}
-  \begin{flushright}
-
-      \begin{prooftree}
-        \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
-        \RightLabel{${\bf ncontr}_2, s \in C$}
-        \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
-      \end{prooftree}
-
-      \begin{prooftree}
-        \AxiomC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
-        \RightLabel{${\bf ex}_2, s \in E$}
-        \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow A$}
-      \end{prooftree}
-
-  \begin{prooftree}
-    \AxiomC{$\Gamma \rightarrow A$}
-    \AxiomC{$\Pi, A, \Delta \rightarrow B$}
-    \RightLabel{${\bf cut}$}
-    \BinaryInfC{$\Gamma, \Pi, \Delta \rightarrow B$}
-  \end{prooftree}
-  \end{flushright}
-\end{minipage}
-\end{defin}
+\end{defin}
+
+After that, we introduce inference polymodal inference rules for non-commutative subexponentials. One can apply substructural
+rules only if there is the relevant index on the current modality. Also, the right introduction rule is a sort of the
+generalised right $\Box$-introduction a la $K4$.
+Modality $!_s$ might be introduced on the right only if its index is less than any other subexponential index from the antecedent.
+That is, if we have already used stronger modality, then we may
+apply the weaker one.
+
+  \vspace{\baselineskip}
+
+Let us consider the current proof-theoretical and algorithmic results on Lambek calculus with additives and subexponentials.
+The first of all, the cut rule is admissible. Generally, this calculus is undecidable, but the fragment without non-local
+contraction is PSPACE-complete. These results were obtained by Kanovich, Kuznetsov, Nigam, and Scedrov.
 
@@
 
-\section{Semantics}
+\section{Quantale background}
+
+Now we introduce a reader to quantales quite briefly. For more details, one may take a look at these books \cite{Quantale18}
+\cite{Rosenthal}. The initial idea of considering quantales in linear logic belongs to Yetter \cite{Yetter}.
 
@@
 
-  A quantale is a triple $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$, such that $\langle A, \bigvee \rangle$
-is a complete lattice and $\langle A, \cdot \rangle$ is a semigroup, such that for all indexing set $I$:
+  A quantale is a triple $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$, where $\langle A, \bigvee \rangle$
+is a complete join semilattice and $\langle A, \cdot \rangle$ is a semigroup such that for each indexing set $I$:
 
@@
 \end{defin}
-
-Some example of quantales:
 
@@
 
+Residuality property for those divisions holds straightforwardly:
+
+\begin{center}
+  $b \leq a \backslash c \Leftrightarrow a \cdot b \leq c \Leftrightarrow a \leq b / c$
+\end{center}
+
 \begin{defin}
@@
 
-  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism if a quantale homomorphism, such that $f(\varepsilon) = \varepsilon$.
-\end{defin}
-
-\begin{defin}
-$ $
-
-  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale. $\mathcal{S} \subseteq \mathcal{Q}$ is said to be a subquantale, if
-  $\mathcal{S}$ is closed under multiplication and sups.
+  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism if a quantale homomorphism such that $f(\varepsilon) = \varepsilon$.
+\end{defin}
+
+\begin{defin}
+$ $
+
+  Let $\mathcal{Q} = \langle A, \bigvee, \cdot \rangle$ be a quantale. $\mathcal{S} \subseteq \mathcal{Q}$ is said to be a subquantale, if $\mathcal{S}$ is closed under multiplication and joins.
 \end{defin}
@@
 Then, if $f : \mathcal{Q}_1 \to \mathcal{Q}_2$ is a quantale homomorphism, then $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a subquantale of $\mathcal{Q}_2$.
-
-In other words, a homomorphic image of subquantale is a subquantale.
 \end{prop}
@@
 
-  It is clearly that $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a submonoid of $\mathcal{Q}_2$. Let $a_i \in S$ for each $i
-  \in I$, so $\bigvee \limits_{i \in I} a_i \in S$, but $f(a_i) \in f(\mathcal{S})$ for any $i \in I$, so $f(\bigvee
-  \limits_{i \in I} a_i) = \bigvee \limits_{i \in I} (f (a)) \in f(\mathcal{S})$, so $f(\mathcal{S})$ is closed
-  under joins, so $f(\mathcal{S})$ is a subquantale of $\mathcal{Q}_2$
+  Follows from the same statements for semigroup and semilattice homomorphisms.
 \end{proof}
@@
 
-\begin{defin}
-$ $
-
-  An open modality (or quantic conucleus) on quantale $\mathcal{Q}$ is a map $\Box : \mathcal{Q} \to \mathcal{Q}$, such that
-
-\begin{enumerate}
-  \item $\Box x \leq x$;
-  \item $\Box x = \Box \Box x$;
-  \item $x \leq y \Rightarrow \Box x \leq \Box y$;
-  \item $\Box x \cdot \Box y = \Box (\Box x \cdot \Box y)$.
-\end{enumerate}
-
-For unital quantale, we require that $\Box e = e$.
-\end{defin}
-
-Note that, we may replace the last condition on equivalent condition $\Box (x) \cdot \Box (y) \leq \Box (x \cdot y)$.
-
-\begin{defin}
-$ $
-
-  We define a partial order on open modalities on $\mathcal{Q}$ as $\Box_1 \leq \Box_2 \Leftrightarrow \forall a \in Q, \Box_1 (a) \leq \Box_2 (a)$.
+We introduce the notion of quantic conucleus, an interior operation on quantale, which is a lax homomorphism with respect to semigroup multiplication.
+For unital quantales, this conucleus preserves a neutral.
+
+\begin{defin}
+$ $
+
+  An open modality (or quantic conucleus) on quantale $\mathcal{Q}$ is a map $I : \mathcal{Q} \to \mathcal{Q}$, such that
+
+\begin{enumerate}
+  \item $I x \leq x$;
+  \item $I x = I^2 x$;
+  \item $x \leq y \Rightarrow I x \leq I y$;
+  \item $I x \cdot I y = I (I x \cdot I y)$.
+\end{enumerate}
+
+For unital quantale, we require that $I e = e$.
+\end{defin}
+
+Here and below, $I^2 x$ denotes $I (I x)$.
+
+Note that, one may replace the last condition on the one $I x \cdot I y \leq I (x \cdot y)$. Thus, a quantic conuleus is the special case of lax monoidal monad from a category-theoretic point of view.
+
+\begin{defin}
+$ $
+
+  We define a partial order on quantic conuclei on $\mathcal{Q}$ as
+  $I_1 \leq I_2 \Leftrightarrow \forall a \in \mathcal{Q}, I_1 a \leq I_2 a$.
 \end{defin}
@@
 \begin{lemma}
-  $\Box_1 a_1 \cdot \Box_2 a_2 \leq \Box (\Box_1 a_1 \cdot \Box_2 a_2)$, where $\Box_i \leq \Box, i = 1,2$.
+  $I_1 a_1 \cdot I_2 a_2 \leq I (I_1 a_1 \cdot I_2 a_2)$, where $I_i \leq I, i = 1,2$.
 \end{lemma}
@@
 
-  $\begin{array}{lll}
-  &\Box_1 a_1 \cdot \Box_2 a_2 \leq & \\
-  &\Box_1 (\Box_1 a_1) \cdot \Box_2 (\Box_2 a_2) \leq & \\
-  &\Box (\Box_1 a_1) \cdot \Box (\Box_2 a_2) \leq & \\
-  &\Box (\Box_1 (a_1) \cdot \Box_2 (a_2))&
-  \end{array}$
-\end{proof}
-
-\begin{defin}
-$ $
-\begin{enumerate}
-  \item An open modality is called central, if for all
+  $I_1 a_1 \cdot I_2 a_2 \leq I_1 (I_1 a_1) \cdot I_2 (I_2 a_2) \leq I (I_1 a_1) \cdot I (I_2 a_2) \leq I (I_1 a_1 \cdot I_2 a_2)$
+\end{proof}
+
+Let us define the special cases of quantic conuclei that it would be useful for our purpose:
+
+\begin{defin}
+$ $
+\begin{enumerate}
+  \item A quantic conucleus is called central, if for all
   $a, b \in \mathcal{Q}, \Box a \cdot b = b \cdot \Box a$.
 
-  \item An open modality is called weak square-increasing,
+  \item A quantic conucleus is called strong square-increasing,
   if for all $a, b \in \mathcal{Q}, \Box a \cdot b \leq \Box a \cdot b \cdot \Box a$ and
@@
 
-  \item An open modality is called unital, if $\forall a \in Q, \Box a \leq e$.
-\end{enumerate}
-\end{defin}
+  \item A quantic conucleus is called unital, if $\forall a \in Q, \Box a \leq e$.
+\end{enumerate}
+\end{defin}
+
+Note that centrality and strong square-increasing yield centrality.
 
@@
 
-  Let $\Box$ be an open modality on some unital quantale $\mathcal{Q} = \langle A, \bigvee, \cdot, e \rangle$.
-  Then, if $\Box$ is unital and weak idempotent, then $\Box$ is central.
+  Let $I$ be an open modality on some unital quantale $\mathcal{Q} = \langle A, \bigvee, \cdot, e \rangle$.
+  Then, if $I$ is unital and weak idempotent, then $I$ is central.
 \end{lemma}
@@
   $\begin{array}{lll}
-  & b \cdot \Box a \leq & \\
-  & \:\:\:\: \text{Right weak square-increase}& \\
-  &\Box a \cdot b \cdot \Box a \leq & \\
-  & \:\:\:\: \text{Unitality}& \\
-  & \Box a \cdot b \cdot e \leq & \\
-  & \:\:\:\: \text{Identity}& \\
-  &\Box a \cdot b \leq & \\
-  & \:\:\:\: \text{Left weak square-increase}& \\
-  &\Box a \cdot b \cdot \Box a \leq & \\
-  & \:\:\:\: \text{Unitality}& \\
-  &e \cdot b \cdot \Box a \leq & \\
-  & \:\:\:\: \text{Identity}& \\
-  &b \cdot \Box a&
+  & b \cdot I a \leq & \\
+  & \:\:\:\:\:\: \text{Right strong square-increase}& \\
+  &I a \cdot b \cdot I a \leq & \\
+  & \:\:\:\:\:\: \text{Unitality}& \\
+  & I a \cdot b \cdot e \leq & \\
+  & \:\:\:\:\:\: \text{Identity}& \\
+  &I a \cdot b \leq & \\
+  & \:\:\:\:\:\: \text{Left strong square-increase}& \\
+  &I a \cdot b \cdot I a \leq & \\
+  & \:\:\:\:\:\: \text{Unitality}& \\
+  &e \cdot b \cdot I a \leq & \\
+  & \:\:\:\:\:\: \text{Identity}& \\
+  &b \cdot I a&
   \end{array}$
 
-Hence, $b \cdot \Box a = \Box a \cdot b$, so for all $a \in \mathcal Q, \Box a \in \mathcal{Z}(\mathcal{Q})$.
+Hence, $b \cdot I a = I a \cdot b$, so for all $a \in \mathcal{Q}, I a \in \mathcal{Z}(\mathcal{Q})$.
 
@@
   Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale,
-  then $\Box : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+  then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
 \end{prop}
@@
 
+We define a subexponential interpretation in a quite sophisticated manner. Suppose we have a contravariant map from signature
+to the set of subquantales. Here, contravariance denotes that the stronger subexponential index (in sense of preorder) maps
+to the weaker subquantale. The second one function maps a subquantale to its quantic conucleus according to the previous
+proposition. We match the index pursuant to its subset. In other words, if $s \in W$, then the result of subexponential
+interpretation is an unital quantic conucleus, etc. More formally:
+
 \begin{defin} Interpretation of subexponential signature
 
-  Let $\Sigma = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature, where $|I| = n$ and
-  $\Box_{\mathcal{Q}}$ is a category of open modalities on a quantale $\mathcal{Q}$.
-  Subexponential interpretation is a contravariant functor $\sigma : I \to \Box_{\mathcal{Q}}$ defined as follows:
+Let $\mathcal{Q}$ be a quantale and $\Sigma = \langle \mathcal{I}, \preceq, \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$ be
+a subexponential signature. Suppose, we have $S : \Sigma \to Sub(\mathcal{Q})$, a contravariant map from this subexponential
+signature to the set of subquantales of $\mathcal{Q}$, and map $M : \mathcal{P}(\mathcal{Q}) \to \Box_{\mathcal{Q}}$, where
+$\Box_{\mathcal{Q}}$ is the set of quantic conuclei on $\mathcal{Q}$. Thus, a subexponential interpretation is the map
+$\sigma = M \circ S$ such that:
 
   $\sigma(s_i) = \begin{cases}
-  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a\},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a\},
   \\ \:\:\:\: \text{if $s_i \notin W \cap C \cap E$} \\
-  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
   \\ \:\:\:\: \text{if $s_i \in W$} \\
-  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
   \\ \:\:\:\: \text{if $s_i \in E$} \\
-  \Box_i : \mathcal{Q} \to \mathcal{Q} \text{, s.t.} \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
   \\ \:\:\:\: \text{if $s_i \in E$} \\
@@
 
+An interpretation and an entailment relation are defined standardly via valuation map and subexponential interpretation. There occur soundness and completeness theorems:
+
 \begin{theorem}
@@
 \begin{proof}
+  $ $
+
 We consider the promotion case, the rest modal cases are immediatly shown.
 
-Let $!_{s_1} A_1, \dots, !_{s_n} A_n \rightarrow A$ and $\forall i, s \preceq s_i$.
-
-Then $\forall a \in Q, \sigma(s_i)(a) \leq \sigma(s)(a)$.
-
-By IH, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq [\![A]\!]$.
-
-Thus, $\sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!]) \leq \sigma(s)([\![A]\!])$.
-
-By Lemma 5, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!])$.
+Let $!_{s_1} A_1, \dots, !_{s_n} A_n \rightarrow A$ and $\forall i, s \preceq s_i$. Then $\forall a \in Q, \sigma(s_i)(a) \leq \sigma(s)(a)$.
+
+By IH, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq [\![A]\!]$. Thus, $\sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!]) \leq \sigma(s)([\![A]\!])$.
+
+By Lemma, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!])$.
 
@@
 
-\section{Quantale completeness}
+Now we prove completeness a la MacNeille completetion. As a matter of fact, we generalised the technique provided by Brown and Gurr for the polymodal case.
 
@@
 \begin{lemma}
-Let $!_s \in I$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$
-  is a quantic conucleus.
+  $ $
+
+\begin{enumerate}
+\item Let $!_s \in I$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$ is a quantic conucleus
+\item Let $A \in \mathcal{F}_{\Sigma}$, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$
+\item  Let $i, j \in I$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
+\end{enumerate}
+
 \end{lemma}
@@
 
-See Yetter.
-\end{proof}
-
-\begin{lemma}
-  Let $A \in \mathcal{F}_{\Sigma}$, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$.
-\end{lemma}
-
-\begin{proof}
-  Let $A \in Fm$ and $s \in \mathcal{I}$.
+\begin{enumerate}
+\item Similarly to [Yetter].
+\item Let $A \in Fm$ and $s \in \mathcal{I}$.
 
@@
 
-  Let $C \in \bigvee \{ !_s A \}$, then $C \rightarrow !_s A$, so $!_s C \rightarrow !_s A$ by dereliction, but $!_s A \rightarrow A$, hence
-  $!_s C \rightarrow A$ by cut. So, $!_s C \in \Box_s \bigvee \{ A \}$.
-\end{proof}
-
-\begin{lemma}
-$ $
-
-  Let $i, j \in I$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
-\end{lemma}
-
-\begin{proof}
-$ $
-
-  Let $i, j \in I$ and $i \preceq j$, then forall $A \in \mathcal{F}_{\Sigma}$, $!_j A \rightarrow !_i A$ by promotion.
+Let $C \in \bigvee \{ !_s A \}$, then $C \rightarrow !_s A$, so $!_s C \rightarrow !_s A$ by dereliction, but $!_s A \rightarrow A$, hence $!_s C \rightarrow A$ by cut.
+So, $!_s C \in \Box_s \bigvee \{ A \}$.
+\item   Let $i, j \in I$ and $i \preceq j$, then forall $A \in \mathcal{F}_{\Sigma}$, $!_j A \rightarrow !_i A$ by promotion.
   Then $\bigvee \{ !_j A \} \subseteq \bigvee \{ !_i A \}$, so $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
+\end{enumerate}
 \end{proof}
@@
 
-Let $\mathcal{Q}$ be a syntactic quantale as proposed above and
-$\mathcal{I} = \langle I, \preceq, W, C, E \rangle$ be a subexponential signature.
+Let $\mathcal{Q}$ be a syntactic quantale defined above and $\mathcal{I} = \langle \mathcal{I}, \preceq,
+\mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$ be a subexponential signature.
 
@@
 \begin{comment}
+
+\section{Categorical part}
 
@@
 
-\begin{theorem}
+\begin{lemma}
   $ $
@@
 
-  Then $\langle \mathcal{Q}, \Box_{\mathcal{S}} \rangle$ is isomorphic to some relational quantale of $A$
-  wit some quantic conucleus $\hat{\Box}$.
-\end{theorem}
+  Then $\langle \mathcal{Q}, I_{\mathcal{S}} \rangle$ is isomorphic to some relational quantale of $A$
+  with some quantic conucleus $\hat{I}$, where $I_{\mathcal{S}}$ is a quantic conclues on $\mathcal{S}$.
+\end{lemma}
 
@@
   Let $\mathfrak{Q} = \langle \mathcal{Q}, I \rangle$ be a quantale with
-  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some quantic conucleus.
+  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some conucleus.
 \end{theorem}
@@
 
-  It is clear that, $I(a) \leq a$. So $I(a) \leq \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = I'(a)$.
-
-  Thus, we showed that $I(a) = I'(a)$. One need to apply the previous theorem with $I'$.
+  On the other hand, $I(a) \leq a$. So $I(a) \leq \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = I'(a)$.
+
+  Thus, we showed that $I(a) = I'(a)$. One need to apply the previous statement with conucleus $I'$.
 \end{proof}
@@
   \begin{enumerate}
-    \item $M \subseteq \mathcal{L}^{*}$, $M^{\triangleright} = \{ (x, y) \: | \: \forall w \in M, x w y \in L \}$;
+    \item $M \subseteq \mathcal{L}^{*}$, $M^{\triangleright} = \{ (x, y) \: | \: \forall w \in M, x w y \in L \}$
     \item $C \subseteq \mathcal{L}^{*} \times \mathcal{L}^{*}$, $C^{\triangleleft} = \{ w \: | \: \forall (x, y) \in C, x w y
@@
 
-We define a product of concepts as $A \circ B = (A \cdot B)^{\triangleright \triangleleft} =
-\{ a b \: | \: a \in A, b \in B \}^{\triangleright \triangleleft}$.
+We define a product of concepts as $A \circ B = (A \cdot B)^{\triangleright \triangleleft} = \{ a b \: | \: a \in A, b \in B \}^{\triangleright \triangleleft}$.
 
@@
 
-It is easy to see, that the following condition hold for that residuals:
+It is easy to see that the following condition hold for that residuals:
 
@@
 \begin{defin}
-  The syntax concept lattice of a language $L$ is a structure $\langle \mathcal{B}_{L}, \circ, \bigvee, \bigwedge, /,
-  \backslash \rangle$, where $\mathcal{B}_{L}$ is the set of $[.]^{\triangleright \triangleleft}$-closed subsets of
-  $\mathcal{L}^{*}$.
+  The syntax concept lattice of a language $L$ is a structure $\langle \mathcal{B}_{L}, \circ, \bigvee, \bigwedge, /, \backslash \rangle$,
+  where $\mathcal{B}_{L}$  is the set of $[.]^{\triangleright \triangleleft}$-closed subsets of $\mathcal{L}^{*}$.
 \end{defin}
@@
 
+\addcontentsline{toc}{section}{Список использованной литературы}
+
+\begin{thebibliography}{}
+
+  \bibitem{Ajdukiewicz} Ajdukiewicz
+
+  \bibitem{Bar} Bar-Hillel
+
+  \bibitem{Lambek} Lambek
+
+  \bibitem{Wilde} Wilde
+\end{thebibliography}
+
 \end{document}

### 2019-06-24 PaperDraft.tex
updates in the draft

@@
 
+\vspace{\baselineskip}
+
 \begin{minipage}{0.5\textwidth}
@@
 
-Also, we have a multiplicative conjunction or non-commutative tensor. This connective plays the role of concatenation.
+\vspace{\baselineskip}
 
@@
 additive connections are intersection and union of languages:
+
+\vspace{\baselineskip}
 
@@
 \end{minipage}
+
+\vspace{\baselineskip}
 
@@
 
-\begin{defin} Noncommutative linear logic with subexponentials ($SMALC_{\Sigma}$), where $\Sigma$ is a subexponential signature.
-
-    \vspace{\baselineskip}
-
-\begin{minipage}{0.5\textwidth}
-  \begin{flushleft}
-    \begin{prooftree}
-    \AxiomC{$\Gamma, A, \Delta \rightarrow C$}
-    \RightLabel{$! \rightarrow$}
-    \UnaryInfC{$\Gamma, !^{s} A, \Delta \rightarrow C$}
-    \end{prooftree}
-
-    \begin{prooftree}
-    \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
-    \RightLabel{${\bf ncontr}_1, s \in C$}
-    \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
-    \end{prooftree}
-
-    \begin{prooftree}
-    \AxiomC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
-    \RightLabel{${\bf ex}_1, s \in E$}
-    \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow A$}
-    \end{prooftree}
-
-  \end{flushleft}
-\end{minipage}
-\begin{minipage}{0.5\textwidth}
-  \begin{flushright}
-    \begin{prooftree}
-    \AxiomC{$!^{s_1} A_1, \dots, !^{s_n} A_n \rightarrow A$}
-    \RightLabel{$\rightarrow !, \forall j, s_j \succeq s$}
-    \UnaryInfC{$!^{s_1} A_1, \dots, !^{s_n} A_n \rightarrow !^{s} A$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
-      \RightLabel{${\bf ncontr}_2, s \in C$}
-      \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
-    \end{prooftree}
-
-    \begin{prooftree}
-      \AxiomC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
-      \RightLabel{${\bf ex}_2, s \in E$}
-      \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow A$}
-    \end{prooftree}
-  \end{flushright}
-\end{minipage}
-
-\begin{prooftree}
-\AxiomC{$\Gamma, \Delta \rightarrow B$}
-\RightLabel{${\bf weak}_!, s \in C$}
-\UnaryInfC{$\Gamma, !^{s} A, \Delta \rightarrow B$}
-\end{prooftree}
-
-\end{defin}
-
-After that, we introduce inference polymodal inference rules for non-commutative subexponentials. One can apply substructural
+Let us introduce inference polymodal inference rules for non-commutative subexponentials. One can apply substructural
 rules only if there is the relevant index on the current modality. Also, the right introduction rule is a sort of the
@@
 
+\begin{defin} Noncommutative linear logic with subexponentials ($SMALC_{\Sigma}$), where $\Sigma$ is a subexponential signature.
+
+    \vspace{\baselineskip}
+
+\begin{minipage}{0.5\textwidth}
+  \begin{flushleft}
+    \begin{prooftree}
+    \AxiomC{$\Gamma, A, \Delta \rightarrow C$}
+    \RightLabel{$! \rightarrow$}
+    \UnaryInfC{$\Gamma, !^{s} A, \Delta \rightarrow C$}
+    \end{prooftree}
+
+    \begin{prooftree}
+    \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
+    \RightLabel{${\bf ncontr}_1, s \in C$}
+    \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
+    \end{prooftree}
+
+    \begin{prooftree}
+    \AxiomC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
+    \RightLabel{${\bf ex}_1, s \in E$}
+    \UnaryInfC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow A$}
+    \end{prooftree}
+
+  \end{flushleft}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+  \begin{flushright}
+    \begin{prooftree}
+    \AxiomC{$!^{s_1} A_1, \dots, !^{s_n} A_n \rightarrow A$}
+    \RightLabel{$\rightarrow !, \forall j, s_j \succeq s$}
+    \UnaryInfC{$!^{s_1} A_1, \dots, !^{s_n} A_n \rightarrow !^{s} A$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma, !^{s} A, \Delta, !^{s} A, \Theta \rightarrow B$}
+      \RightLabel{${\bf ncontr}_2, s \in C$}
+      \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow B$}
+    \end{prooftree}
+
+    \begin{prooftree}
+      \AxiomC{$\Gamma, !^{s} A, \Delta, \Theta \rightarrow B$}
+      \RightLabel{${\bf ex}_2, s \in E$}
+      \UnaryInfC{$\Gamma, \Delta, !^{s} A, \Theta \rightarrow A$}
+    \end{prooftree}
+  \end{flushright}
+\end{minipage}
+
+\begin{prooftree}
+\AxiomC{$\Gamma, \Delta \rightarrow B$}
+\RightLabel{${\bf weak}_!, s \in C$}
+\UnaryInfC{$\Gamma, !^{s} A, \Delta \rightarrow B$}
+\end{prooftree}
+
+\end{defin}
+
   \vspace{\baselineskip}
@@
 The first of all, the cut rule is admissible. Generally, this calculus is undecidable, but the fragment without non-local
-contraction is PSPACE-complete. These results were obtained by Kanovich, Kuznetsov, Nigam, and Scedrov.
+contraction is PSPACE-complete. These results were obtained by Kanovich, Kuznetsov, Nigam, and Scedrov \cite{Sc}.
 
@@
 
-\begin{defin}
-$ $
-
-  We define a partial order on quantic conuclei on $\mathcal{Q}$ as
-  $I_1 \leq I_2 \Leftrightarrow \forall a \in \mathcal{Q}, I_1 a \leq I_2 a$.
-\end{defin}
-
-\begin{lemma}
-  $I_1 a_1 \cdot I_2 a_2 \leq I (I_1 a_1 \cdot I_2 a_2)$, where $I_i \leq I, i = 1,2$.
-\end{lemma}
-
-\begin{proof}
-$ $
-
-  $I_1 a_1 \cdot I_2 a_2 \leq I_1 (I_1 a_1) \cdot I_2 (I_2 a_2) \leq I (I_1 a_1) \cdot I (I_2 a_2) \leq I (I_1 a_1 \cdot I_2 a_2)$
-\end{proof}
-
 Let us define the special cases of quantic conuclei that it would be useful for our purpose:
@@
 
-Note that centrality and strong square-increasing yield centrality.
+\begin{defin}
+$ $
+
+  We define a partial order on quantic conuclei on $\mathcal{Q}$ as
+  $I_1 \leq I_2 \Leftrightarrow \forall a \in \mathcal{Q}, I_1 a \leq I_2 a$.
+\end{defin}
+
+Here we formulate and prove some techincal lemmas on quantic conuclei that we apply in the proof of soundness and completeness theorems:
 
@@
   $ $
-
-  Let $I$ be an open modality on some unital quantale $\mathcal{Q} = \langle A, \bigvee, \cdot, e \rangle$.
-  Then, if $I$ is unital and weak idempotent, then $I$ is central.
+  Let $\mathcal{Q}$ be a quantale. Let $I$, $I_1$, and $I_2$ be quantic conuclei. Thus, the following properties hold:
+  \begin{enumerate}
+  \item $I_1 a_1 \cdot I_2 a_2 \leq I (I_1 a_1 \cdot I_2 a_2)$, where $I_i \leq I, i = 1,2$.
+  \item If $I$ is unital and weak idempotent, then $I$ is central.
+  \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+  \item Let $S_1$ and $S_2$ are subquantales such that $mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$. Then $\Box_{\mathcal{S}_1} (a) \leq \Box_{\mathcal{S}_1} (a)$.
+  \end{enumerate}
 \end{lemma}
@@
 $ $
+
+\begin{enumerate}
+  \item $I_1 a_1 \cdot I_2 a_2 \leq I_1 (I_1 a_1) \cdot I_2 (I_2 a_2) \leq I (I_1 a_1) \cdot I (I_2 a_2) \leq I (I_1 a_1 \cdot I_2 a_2)$
+  \item $ $
 
@@
   Hence, $b \cdot I a = I a \cdot b$, so for all $a \in \mathcal{Q}, I a \in \mathcal{Z}(\mathcal{Q})$.
-
+  \item See Rosental.
+  \item Immediately.
+\end{enumerate}
 \end{proof}
@@
 
-  Let $\mathcal{Q}$ be a quantale and $S \subseteq \mathcal{Q}$ a subquantale,
-  then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+Let $\mathcal{Q}$ be a quantale and $\mathcal{S} \subseteq \mathcal{Q}$ a subquantale, then the following operations are open modalities:
+
+\begin{enumerate}
+  \item $I a = \bigvee \{ s \in S \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \}$ is a central quantic conucleus
+  \item $I a = \bigvee \{ s \in S \: | \: s \leq a, s \leq \mathds{1} \}$ is an unital conucleus
+  \item $I a = \bigvee \{ s \in S \: | \: s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$ is a generalised square-increasing quantic conucleus
+  \item Operations with combinations of conditions above
+\end{enumerate}
 \end{prop}
@@
 \begin{proof}
-  See Rosenthal.
+  Immediately
 \end{proof}
@@
 $ $
-
-  Let $\mathcal{Q}$ be a quantale and $\mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$.
-
-  Then $\Box_{\mathcal{S}_1} (a) \leq \Box_{\mathcal{S}_1} (a)$.
+Let $\mathcal{Q}$ be a quantale, then:
+\begin{enumerate}
+  \item Let $I_1$ be a unital and generalised square-increasing and $I_2$ a central, then $\forall a \in \mathcal{Q}, I_1 a \leq I_2 a$
+  \item If $I_1$ is GSI, unital, and central, $I_2$ is GSI and unital, then $\forall a \in \mathcal{Q}, I_1 a = I_2 a$
+\end{enumerate}
+
 \end{prop}
@@
 \begin{proof}
-
-Immediatly.
-\end{proof}
-
-\begin{prop}
-$ $
-
-Let $\mathcal{Q}$ be a quantale and $\mathcal{S} \subseteq \mathcal{Q}$ a subquantale, then the following operations are open modalities:
-
-\begin{enumerate}
-  \item $\Box_z (a) = \bigvee \{ s \in S \: | s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \}$;
-  \item $\Box_{\mathds{1}} (a) = \bigvee \{ s \in S \: | s \leq a, s \leq \mathds{1} \}$;
-  \item $\Box_{idem} (a) = \bigvee \{ s \in S \: | s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$;
-  \item Operations with combinations of conditions above;
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-  Immediatly.
-\end{proof}
-
-\begin{prop}
-$ $
-
-\begin{enumerate}
-  \item $\forall a \in \mathcal{Q}, \Box_{\mathds{1}, idem}(a) \leq \Box_z (a)$.
-  \item $\forall a \in \mathcal{Q}, \Box_{z, \mathds{1}, idem} = \Box_{\mathds{1}, idem}(a)$
-\end{enumerate}
-
-\end{prop}
-
-\begin{proof}
-  Follows from Lemma 3.
-\end{proof}
-
-We define a subexponential interpretation in a quite sophisticated manner. Suppose we have a contravariant map from signature
-to the set of subquantales. Here, contravariance denotes that the stronger subexponential index (in sense of preorder) maps
-to the weaker subquantale. The second one function maps a subquantale to its quantic conucleus according to the previous
-proposition. We match the index pursuant to its subset. In other words, if $s \in W$, then the result of subexponential
-interpretation is an unital quantic conucleus, etc. More formally:
+$ $
+
+  \begin{enumerate}
+    \item Follows from Lemma 1.2.
+    \item The right inequation follows from the first of this lemma. The left inequation is obvious.
+  \end{enumerate}
+\end{proof}
+
+We define a subexponential interpretation in quite sophisticatedly.
+Suppose we have a contravariant map from a given signature to the set of subquantales.
+Here, contravariance denotes that the stronger subexponential index (in sense of
+preorder) maps to the weaker subquantale. The second one function maps a subquantale to its quantic conucleus according to
+the previous proposition. We match the index pursuant to its subset. In other words, if $s \in W$, then the result of s
+subexponential interpretation is an unital quantic conucleus, etc. More formally:
 
@@
 
-Let $\mathcal{Q}$ be a quantale and $\Sigma = \langle \mathcal{I}, \preceq, \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$ be
-a subexponential signature. Suppose, we have $S : \Sigma \to Sub(\mathcal{Q})$, a contravariant map from this subexponential
-signature to the set of subquantales of $\mathcal{Q}$, and map $M : \mathcal{P}(\mathcal{Q}) \to \Box_{\mathcal{Q}}$, where
-$\Box_{\mathcal{Q}}$ is the set of quantic conuclei on $\mathcal{Q}$. Thus, a subexponential interpretation is the map
-$\sigma = M \circ S$ such that:
+Let $\mathcal{Q}$ be a quantale and $\Sigma = \langle \mathcal{I}, \preceq, \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$
+a subexponential signature. Let $S : \Sigma \to Sub(\mathcal{Q})$ be a contravariant map from this subexponential
+signature to the set of subquantales of $\mathcal{Q}$ Thus, a subexponential interpretation is the map
+$\sigma : \Sigma \to CN(\mathcal{Q})$, where $CN(\mathcal{Q})$ is the set of quantic conuclei on $\mathcal{Q}$, such that:
 
@@
 
-An interpretation and an entailment relation are defined standardly via valuation map and subexponential interpretation. There occur soundness and completeness theorems:
+An interpretation and an entailment relation are defined standardly via valuation map and subexponential interpretation.
+The first of all, let us make sure that any subexponential interpretation is sound w.r.t the set of quantic conuclei $CN(\mathcal{Q})$ of the quantale $\mathcal{Q}$.
+
+\begin{lemma}
+  $ $
+
+  Let $\Sigma$ be a subexponential signature and $\sigma : \Sigma \to CN(\mathcal{Q})$ for a contravariant map
+  $S : \Sigma \to Sub(\mathcal{Q})$, then:
+  \begin{enumerate}
+  \item For all $s_1, s_2 \in \Sigma$, if $s_1 \preceq s_2$, then $\sigma(s_2) \leq \sigma(s_1)$.
+  In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
+  \item $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
+  \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+  $ $
+
+  \begin{enumerate}
+  \item Let $s_1, s_2 \in \Sigma$ and $s_1 \leq s_2$. Then $S(s_2) \subseteq S(s_1)$.
+  So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
+  \item Let $s_1 \in A$ and $s_1 \preceq s_2$.
+By the previous part, $\sigma(s_2) \leq \sigma(s_1)$.
+Suppose $\sigma(s_2) \notin \sigma(A)$, then $s_2 \notin A$.
+But $s_2 \in A$ so far as $A$ is upwardly closed.
+Contradiction.
+  \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
+  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \in \mathcal{Z}(\mathcal{Q}), \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$.
+Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.
+
+\end{enumerate}
+\end{proof}
+
+There occur soundness and completeness theorems.
 
 \begin{theorem}
-  $\Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$
+$ $
+
+  Let $\Sigma$ be a subexponential signature, then
+  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for some valuation map $f$ and subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
 \end{theorem}
@@
 
-We consider the promotion case, the rest modal cases are immediatly shown.
+By the previous lemma, $\sigma$ is well-defined. Let us consider the case of polymodal promotion.
 
@@
 
-By IH, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq [\![A]\!]$. Thus, $\sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!]) \leq \sigma(s)([\![A]\!])$.
-
-By Lemma, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!])$.
-
+By IH, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq [\![A]\!]$. Thus,
+$\sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!]) \leq \sigma(s)([\![A]\!])$. By Lemma,
+$\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)(\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot
+\sigma(s_n) [\![A_n]\!])$. \\
 So, $\sigma(s_1)[\![A_1]\!] \cdot \dots \cdot \sigma(s_n) [\![A_n]\!] \leq \sigma(s)([\![A]\!])$.
@@
 
-  On the other hand, $I(a) \leq a$. So $I(a) \leq \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = I'(a)$.
+  On the other hand, $I(a) \leq a$. So $I(a) \leq \bigvee \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \} = I'(a)$, so far as $I(a) \in \{ s \in \mathcal{Q}_{I} \: | \: s \leq a \}$.
 
@@
 
-Author would like to thank Lev Beklemishev, Stepan Kuznetsov, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov
-for advice, critique, and comments.
-
-\addcontentsline{toc}{section}{Список использованной литературы}
+Author would like to thank Lev Beklemishev, Giuseppe Greco, Stepan Kuznetsov, Jean-Francois Mascari, Fedor Pakhomov, Danyar Shamkanov, and Andre Scedrov for advice, critique, and comments.
+
+\addcontentsline{toc}{section}{References}
 

### 2019-06-24 PaperDraft.tex
updates

@@
   Let $\Sigma$ be a subexponential signature, then
-  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for some valuation map $f$ and subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
+  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for valuation map $f$ and for some subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
 \end{theorem}

### 2019-06-24 PaperDraft.tex
updates in soundness

@@
 \begin{enumerate}
-  \item A quantic conucleus is called central, if for all
-  $a, b \in \mathcal{Q}, \Box a \cdot b = b \cdot \Box a$.
+  \item A quantic conucleus $I$ is called central, if for all
+  $a, b \in \mathcal{Q}, I a \cdot b = b \cdot I a$.
 
   \item A quantic conucleus is called strong square-increasing,
-  if for all $a, b \in \mathcal{Q}, \Box a \cdot b \leq \Box a \cdot b \cdot \Box a$ and
-  $b \cdot \Box a \leq \Box a \cdot b \cdot \Box a$.
+  if for all $a, b \in \mathcal{Q}, I a \cdot b \leq I a \cdot b \cdot I a$ and
+  $b \cdot I a \leq I a \cdot b \cdot I a$.
 
@@
 
+\begin{lemma}
+$ $
+
+  \begin{enumerate}
+    \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+    \item Let $S_1$ and $S_2$ are subquantales such that $\mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$.
+Then $I_{\mathcal{S}_1} (a) \leq I_{\mathcal{S}_1} (a)$, where $I_{\mathcal{S}_i}, i = 1,2$ are quantic conucleis defined according to the previous part.
+  \end{enumerate}
+\end{lemma}
+
+\begin{proof}
+  Immediately
+\end{proof}
+
+\newpage
+
+\begin{lemma} Let $I$ be a quantic conucleus, then for all $a \in \mathcal{Q}$, $I a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$, where $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$.
+\end{lemma}
+
+\begin{proof}
+$ $
+
+So far as $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$ is a subquantale, then $I' a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$ is a quantic conucleus.
+Let us show that these operations are equavalent.
+
+From the one hand,
+
+$\begin{array}{lll}
+&\bigvee \{ q \in Q_{I} \: | \: s \leq a \} = & \\
+& \:\:\:\:\:\:\:\: \text{$s \in Q_{I}$, so s is a fixpoint of $I$} & \\
+&\bigvee \{ q \in Q_{I} \: | \: I s \leq a \} = & \\
+& \:\:\:\:\:\:\:\: \text{By equivalence}& \\
+&\bigvee \{ q \in Q_{I} \: | \: I s \leq I a \} = & \\
+& \:\:\:\:\:\:\:\: \text{By fixpoint} & \\
+&\bigvee \{ q \in Q_{I} \: | \: s \leq I a \} \leq I a& \\
+\end{array}$
+
+On the other hand, $I a \leq a$, then $I a \in \{ q \in Q_{I} \: | \: q \leq a \}$, so far as $I a \in Q_{I}$ (by idempotence). Thus, $I a \leq \bigvee \{ q \in Q_{I} \: | \: q \leq a \}$.
+
+\end{proof}
+
+\begin{lemma}
+$ $
+
+Let $I_1$ be a quantic conucleus $I_2$ a unital (central, strong weak increasing) quantic conucleus such that $I_1 \leq I_2$,
+then $I_1$ is a unital (central, strong weak increasing).
+
+\end{lemma}
+
+\begin{proof}
+  $ $
+
+\begin{enumerate}
+  \item Let $a \in \mathcal{Q}$ (here $\mathcal{Q}$ is supposed to be a unital).
+  Then $I_2 a \leq \varepsilon$, but $I_1 \leq I_2$, so $I_1 a \leq I_2 a$. By transitivity, $I_1 a \leq \varepsilon$.
+  \item Let $a \in \mathcal{Q}$ and $I_2$ is a central quantic conucleus. Let $I_1$ be a quantic conucleus and $I_1 \leq I_2$.
+
+  Thus, $I_2 a \in \mathcal{Z}(\mathcal{Q})$ and, obviously, $Q_{I_2} \subseteq \mathcal{Z}(\mathcal{Q})$.
+
+  Let $b \in Q_{I_1}$, then $b = I_1 b \leq I_2 b \leq b$. Thus, $b = I_2 b$ and $b \in Q_{I_2}$. So, $Q_{I_1} \subseteq \mathcal{Z}(\mathcal{Q})$.
+
+  Let us check that $I_1$ commutes with each other element $d \in \mathcal{Q}$
+
+  $\begin{array}{lll}
+  & I_1 a \cdot d = \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} \cdot d = & \\
+  & \:\:\:\:\:\:\:\: \text{By quantale axiom}& \\
+  & \bigvee \{ q \cdot d \: | \: q \in Q_{I_1} \: \& \: q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{As we proved, $q \in \mathcal{Z}(\mathcal{Q})$} & \\
+  & \bigvee \{ d \cdot q \: | \: q \in Q_{I_1} \: \& \: q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{By quantale axiom}& \\
+  & d \cdot \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{By Lemma \# n}& \\
+  & d \cdot I_1 a &
+  \end{array}$
+
+  \item Let $I_2$ be a strong square increasing. Then, for all $a \in \mathcal{Q}$ and $b \in Q_{I_2}$,
+  $a \cdot b \leq b \cdot a \cdot b$ and $b \cdot a \leq b \cdot a \cdot b$.
+
+  Let $c \in Q_{I_1}$. Similarly to the previous part, $c = I_1 c \leq I_2 c \leq c$, then $c \in Q_{I_2}$ and
+  $I_1$ is a strong square increasing.
+\end{enumerate}
+\end{proof}
+
 Here we formulate and prove some techincal lemmas on quantic conuclei that we apply in the proof of soundness and completeness theorems:
@@
   \item If $I$ is unital and weak idempotent, then $I$ is central.
-  \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
-  \item Let $S_1$ and $S_2$ are subquantales such that $mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$. Then $\Box_{\mathcal{S}_1} (a) \leq \Box_{\mathcal{S}_1} (a)$.
   \end{enumerate}
@@
   Hence, $b \cdot I a = I a \cdot b$, so for all $a \in \mathcal{Q}, I a \in \mathcal{Z}(\mathcal{Q})$.
-  \item See Rosental.
-  \item Immediately.
 \end{enumerate}
@@
 
+  \begin{enumerate}
+    \item $s \in \mathcal{W}$, then $\sigma(s)$ is a unital modality.
+    \item $s \in \mathcal{E}$, then $\sigma(s)$ is a central modality.
+    \item $s \in \mathcal{C}$, then $\sigma(s)$ is GSI modality.
+  \end{enumerate}
+\end{lemma}
+
+\begin{proof}
+  By construction.
+\end{proof}
+
+\begin{lemma}
+  Let $s_1 \in \mathcal{W}$ and $s_1 \preceq s_2$, then $\sigma(s_2)$ is a central modality.
+\end{lemma}
+
+\begin{proof}
+\end{proof}
+
+\begin{lemma}
+  $ $
+
   Let $\Sigma$ be a subexponential signature and $\sigma : \Sigma \to CN(\mathcal{Q})$ for a contravariant map
@@
   In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
-  \item $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
+  $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
   \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
@@
   So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
+  \item
   \item Let $s_1 \in A$ and $s_1 \preceq s_2$.
@@
   \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
-  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \in \mathcal{Z}(\mathcal{Q}), \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$.
+  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \leq \varepsilon, \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$.
 Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.

### 2019-06-24 PaperDraft.tex
updates in quantic conuclei proofs

@@
 
-\newpage
-
 \begin{lemma} Let $I$ be a quantic conucleus, then for all $a \in \mathcal{Q}$, $I a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$, where $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$.
@@
   Let $c \in Q_{I_1}$. Similarly to the previous part, $c = I_1 c \leq I_2 c \leq c$, then $c \in Q_{I_2}$ and
-  $I_1$ is a strong square increasing.
+  $I_1$ is a strong square increasing:
+
+  $\begin{array}{lll}
+  &I_1 a \cdot b = \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} \cdot b = & \\
+  & \:\:\:\:\:\:\:\: \text{By quantale axiom}& \\
+  & \bigvee \{ q \cdot b \: | \: q \in Q_{I_1}, q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{As we proved above}& \\
+  & \bigvee \{ I_2 q \cdot b \: | \: q \in Q_{I_1}, q \leq a \} \leq & \\
+  & \:\:\:\:\:\:\:\: \text{By condition}& \\
+  & \bigvee \{ I_2 q \cdot b \cdot I_2 q \: | \: q \in Q_{I_1}, q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{So far as $q$ is a fixpoint of $I_2$} & \\
+  & \bigvee \{ q \cdot b \cdot q \: | \: q \in Q_{I_1}, q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{By quantale axiom} = & \\
+  & \bigvee \{ q \cdot b \: | \: q \in Q_{I_1}, q \leq a \} \cdot \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{By quantale axiom} = & \\
+  & \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} \cdot b \cdot \bigvee \{ q \in Q_{I_1} \: | \: q \leq a \} = & \\
+  & \:\:\:\:\:\:\:\: \text{By Lemma } = & \\
+  &I_1 a \cdot b \cdot I_1&
+  \end{array}$
+
+  The second inequation might be proved similarly.
 \end{enumerate}

### 2019-07-03 PaperDraft.tex
updates in draft

@@
 
-  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism if a quantale homomorphism such that $f(\varepsilon) = \varepsilon$.
+  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism is a quantale homomorphism such that $f(\varepsilon) = \varepsilon$.
 \end{defin}
@@
   $\sigma(s_i) = \begin{cases}
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a\},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a\},
   \\ \:\:\:\: \text{if $s_i \notin W \cap C \cap E$} \\
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
   \\ \:\:\:\: \text{if $s_i \in W$} \\
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
   \\ \:\:\:\: \text{if $s_i \in E$} \\
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
   \\ \:\:\:\: \text{if $s_i \in E$} \\
@@
 
-\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : I \to \Box_{\mathcal{Q}}$ a subexponential interpretation, then
-  interpretation is defined inductively:
+\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : I \to CN(\mathcal{Q})$ a subexponential interpretation, then interpretation is defined inductively:
 
@@
 
-\begin{lemma}
-  $ $
-
-  \begin{enumerate}
-    \item $s \in \mathcal{W}$, then $\sigma(s)$ is a unital modality.
-    \item $s \in \mathcal{E}$, then $\sigma(s)$ is a central modality.
-    \item $s \in \mathcal{C}$, then $\sigma(s)$ is GSI modality.
-  \end{enumerate}
-\end{lemma}
+\begin{prop} $s \in A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$ iff $\sigma(s)$ is a unital (central or square increasing) modality.
+\end{prop}
 
@@
   By construction.
-\end{proof}
-
-\begin{lemma}
-  Let $s_1 \in \mathcal{W}$ and $s_1 \preceq s_2$, then $\sigma(s_2)$ is a central modality.
-\end{lemma}
-
-\begin{proof}
 \end{proof}
@@
   In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
+  \item Let $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$, then $A$ is downwardly closed
   $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
@@
   So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
-  \item
-  \item Let $s_1 \in A$ and $s_1 \preceq s_2$.
-By the previous part, $\sigma(s_2) \leq \sigma(s_1)$.
-Suppose $\sigma(s_2) \notin \sigma(A)$, then $s_2 \notin A$.
-But $s_2 \in A$ so far as $A$ is upwardly closed.
-Contradiction.
+  \item Let $\sigma(s) \in \sigma(A)$ and $\sigma(s_1) \leq \sigma(s)$, then $\sigma(s)$ is a unital (central or square increasing).
+By Lemma 3, $\sigma(s_1)$ is a unital (central or square increasing) too.
+Thus, $s_1 \in A$ and $\sigma(s_1) \in \sigma(A)$.
   \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
-  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \leq \varepsilon, \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$.
-Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.
+  then $\sigma(s)(a)$. Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.
 
@@
   Let $\Sigma$ be a subexponential signature, then
-  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for valuation map $f$ and for some subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
+  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$.
 \end{theorem}
@@
 
-By the previous lemma, $\sigma$ is well-defined. Let us consider the case of polymodal promotion.
+Let $\sigma$ be a subexponential interpretation. By the previous lemma, $\sigma$ is well-defined. Let us consider the case of polymodal promotion.
 
@@
   \item $\bigvee S$ is an ideal;
-  \item $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$;
+  \item $A \subseteq Fm$, then $\bigvee \{ A \} = \{ B \: | \: B \rightarrow A \} = $;
   \item $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$;
@@
 
-\begin{enumerate}
-\item Let $!_s \in I$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$ is a quantic conucleus
+Let $\Sigma$ be a subexponential signature.
+  \begin{enumerate}
+  \item Let $s \in \Sigma$, then $!_s Syn = \{ \bigvee !_s S \: | \: S \subseteq Fm \}$ is a subquantale.
+  \item Let $\Sigma$ be a subexponential signature, then a map $S : \Sigma \to Sub(Syn)$ such that $S(s) = !_s Syn$ is a contravariant map
+  \end{enumerate}
+\end{lemma}
+
+\begin{proof}
+$ $
+
+\begin{enumerate}
+    \item One need to check that $!_s Syn = \{ \bigvee !_s S \: | \: S \subseteq Fm \}$ is closed under product and sups.
+Let us show that $!_s Syn$ is closed under product, so far as $!_s Syn$ is closed under sups by construction.
+
+    Let $\bigvee !_s X, \bigvee !_s Y \in !_s Syn$. Then $\bigvee !_s X \cdot \bigvee !_s Y = \bigvee (!_s X \cdot !_s Y) \in !_s Syn$, so far as $!_s X \cdot !_s Y \subseteq Fm$.
+
+    \item Let $s_1 \preceq s_2$ and $\bigvee !_{s_2} X \in \: !_{s_2} Syn$. Let us show that $\bigvee !_{s_2} X \in !_{s_1} Syn$.
+
+    $\begin{array}{lll}
+    & \bigvee !_{s_2} X = \{ !_{s_2} B \: | \: !_{s_2} B \to A, A \in X \} = & \\
+    & \{ !_{s_2} B \: | \: !_{s_2} B \to !_{s_2} A, A \in X \} \subseteq & \\
+    & \{ !_{s_2} B \: | \: !_{s_2} B \to !_{s_2} A, A \in X \} \subseteq \bigvee !_{s_1} X& \\
+    \end{array}$
+  \end{enumerate}
+\end{proof}
+
+\begin{lemma}
+  $ $
+
+Let $\Sigma$ be a subexponential signature.
+
+\begin{enumerate}
+\item Let $!_s \in \Sigma$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$ is a quantic conucleus
 \item Let $A \in \mathcal{F}_{\Sigma}$, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$
-\item  Let $i, j \in I$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
+\item  Let $i, j \in \Sigma$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
 \end{enumerate}
@@
 \item Similarly to [Yetter].
-\item Let $A \in Fm$ and $s \in \mathcal{I}$.
+\item Let $A \in Fm$ and $s \in \Sigma$.
 
@@
 
-Let $\mathcal{Q}$ be a syntactic quantale defined above and $\mathcal{I} = \langle \mathcal{I}, \preceq,
+Let $\mathcal{Q}$ be a syntactic quantale defined above and $\Sigma = \langle I, \preceq,
 \mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$ be a subexponential signature.
 
-We define a map $\Box : \mathcal{I} \to Mod_{\mathcal{Q}}$ as follows:
-
-$\Box(i)(\bigvee \{ A \} ) = \{ !_i B \: | !_i B \rightarrow A \}$.
+We define a map $\Box : \mathcal{I} \to Sub(Syn)$ as follows:
+
+$\Box(s)(\bigvee \{ A \} ) = \{ !_s B \in !_s Syn \: | !_i B \rightarrow A \}$.
 \end{defin}
@@
   Let $\mathfrak{Q} = \langle \mathcal{Q}, I \rangle$ be a quantale with
-  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some conucleus.
+  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some conucleus operator.
 \end{theorem}

### 2019-07-03 RModels.tex
representation theorem
updates in draft

@@
 
+As usual, if $V = \{ x \}$ is a singleton, then $\mathcal{F} \restriction x = \langle W \restriction x, R \cap x \rangle$ is a rooted frame (model).
+
 \begin{lemma}
@@
 
-\begin{col}
+\begin{defin}
   $ $
 
-  Let $\mathcal{F}$ be a frame and $\mathcal{F} \restriction V$ is a generated subframe of $\mathcal{F}$.
-  Then $Log(\mathcal{F}) = Log(\mathcal{F} \restriction V)$.
-\end{col}
+  By $L^{*}_{\bf S4}$ ($L_{\bf S4}$) we mean the calculus $L^{*}$ ($L$) extended with the following inference rules:
+
+  \begin{minipage}{0.5\textwidth}
+  \begin{flushleft}
+    \begin{prooftree}
+    \AxiomC{$\Gamma, A, \Delta \rightarrow B$}
+    \RightLabel{$! \to$}
+    \UnaryInfC{$\Gamma, !A, \Delta \rightarrow B$}
+    \end{prooftree}
+  \end{flushleft}
+  \end{minipage}\hfill
+  \begin{minipage}{0.5\textwidth}
+  \begin{flushright}
+    \begin{prooftree}
+    \AxiomC{$! \Gamma \rightarrow A$}
+    \RightLabel{$\to !$}
+    \UnaryInfC{$! \Gamma \rightarrow ! A$}
+    \end{prooftree}
+  \end{flushright}
+  \end{minipage}
+\end{defin}
+
+\begin{prop}
+$ $
+
+$L_{\bf S4}$ ($L^{*}_{\bf S4}$) might be equivalently defined as $L_{\bf S4}^{'} (L^{*}_{\bf S4}) = L (L^{*}) \: \oplus \: ! A \to A \: \oplus \: ! A \to !! A$ closed under monotonicity $!$-rule
+
+\end{prop}
+
+\begin{proof}
+  \item It is clear that $L_{\bf S4} \subseteq L_{\bf S4}^{'}$. The converse inclusion is proved straightforwardly as follows:
+
+\begin{minipage}{0.5\textwidth}
+\begin{flushleft}
+  \begin{prooftree}
+    \AxiomC{$! A \to A$}
+    \AxiomC{$\Gamma, A, \Delta \to A$}
+    \RightLabel{{\bf cut}}
+    \BinaryInfC{$\Gamma, ! A, \Delta \rightarrow B$}
+  \end{prooftree}
+\end{flushleft}
+\end{minipage}\hfill
+\begin{minipage}{0.5\textwidth}
+\begin{flushright}
+  \begin{prooftree}
+    \AxiomC{$ \{ ! A_i \to ! ! A_i \}_{i = 1, \dots, n} $}
+    \AxiomC{$! A_1, ! A_2, \dots, ! A_n \rightarrow B$}
+    \RightLabel{{\bf mon}}
+    \UnaryInfC{$!! A_1, !! A_2, \dots, !! A_n \rightarrow ! B$}
+    \RightLabel{{\bf cut}}
+    \BinaryInfC{$! A_1, ! A_2, \dots, ! A_n \rightarrow ! B$}
+  \end{prooftree}
+\end{flushright}
+\end{minipage}
+\end{proof}
+
+\begin{defin}
+
+  $ $
+
+  A modal $R$-model $\mathfrak{M}$ is a $R$-model with additional truth condition:
+
+  $\mathfrak{M}, \langle a, b \rangle \models ! A \Leftrightarrow \exists {R_1}_{\langle a, b \rangle} \subseteq R \text{ such that } \forall w \in R_1 \: \mathfrak{M}, w \models A$
+\end{defin}
+
+\begin{theorem}
+  Let $R \subseteq W \times W$ be a (reflexive) transitive relation and $\mathcal{F} = \langle W, R \rangle$ a modal $R$-model, then $L_{\bf S4} \subseteq Log(F)$.
+\end{theorem}
+
+  We prove this theorem modulo the previous proposition for simplicity.
+
+\begin{proof}
+
+  \begin{enumerate}
+    \item Let $\mathcal{F} \models \: ! A$, then for all $\langle a, b \rangle \in R$ and for each valuation $v$,
+    $\langle \mathcal{F}, v \rangle, \langle a, b \rangle \models ! A$. Thus, $\langle \mathcal{F}, v \rangle, \langle a, b \rangle \models A$.
+    \item Let $\mathcal{F} \models \: ! A$, then for all $\langle a, b \rangle \in R$, $\langle \mathcal{F}, v \rangle, \langle a, b \rangle \models ! A$,
+    where $v$ is a valuation. It means that there exists $U_{\langle a, b \rangle} \subseteq R$ such that for each $u \in U$,
+    $\langle \mathcal{F}, v \rangle, u \models A$.
+  \end{enumerate}
+\end{proof}
+
+\begin{lemma}
+  Let $\mathcal{F}_1 = \langle W_1, R_1 \rangle$ and $\mathcal{F}_2 = \langle W_2, R_2 \rangle$ be $R$-frames and $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ a $p$-morphism.
+Then $p$-morphism properties also hold
+\end{lemma}
+
+\begin{proof}
+  $ $
+
+  Let us show that $\langle \mathcal{F}_1, v_1 \rangle, \langle a, b \rangle \models ! A \Leftrightarrow \langle \mathcal{F}_2, v_2 \rangle, \langle f(a), f(b) \rangle \models ! A$
+
+    $(\Rightarrow)$ Let $\langle \mathcal{F}_1, v_1 \rangle, \langle a, b \rangle \models ! A$. Then there exists a subrelation $R_1$ such that $\langle a, b \rangle$ and
+    for each $p \in R_1, \langle \mathcal{F}_1, v_1 \rangle, p \models A$.
+    Let us define $R_1^{'} = \{ \langle f(x), f(y) \rangle \: | \: \langle x, y \rangle \in R_1 \} \subseteq R_2$. By IH, for each $p^{'} \in R_1^{'}$,
+    $\langle \mathcal{F}_1, v_1 \rangle, p \models A$.
+Thus, there exists a subrelation that contains $\langle f(a), f(b) \rangle$ in each pair of which $A$ is true.
+So, $\langle \mathcal{F}_2, v_2 \rangle, \langle f(a), f(b) \rangle \models !
+A$.
+
+    $(\Leftarrow)$ Let $\langle \mathcal{F}_2, v_2 \rangle, \langle f(a), f(b) \rangle \models !
+A$.
+Then there exists $R_2^{'} \subseteq R_2$ such that $\langle f(a), f(b) \rangle \in R_2^{'}$ and for each $\langle c, d \rangle$, $\langle \mathcal{F}_2, v_2 \rangle, \langle c, d \rangle \models A$.
+
+\end{proof}
 

### 2019-07-05 PaperDraft.tex
fixes

@@
 
-  $\mathcal{F}_{\Sigma} ::= Tp \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash
-  \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: | ({!_s \mathcal{F}_{\Sigma}})_{s \in
-  \Sigma} $
-\end{defin}
-
-Let us introduce inference polymodal inference rules for non-commutative subexponentials. One can apply substructural
+  $\mathcal{F}_{\Sigma} ::= Tp \: | \: {\bf 1} \: | \: (\mathcal{F}_{\Sigma} / \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \backslash
+  \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \bullet \mathcal{F}_{\Sigma}) \: | \: (\mathcal{F}_{\Sigma} \lor \mathcal{F}_{\Sigma}) \: | (\mathcal{F}_{\Sigma} \land \mathcal{F}_{\Sigma}) \: |
+   \: ({!_s \mathcal{F}_{\Sigma}})_{s \in \Sigma} $
+\end{defin}
+
+Let us introduce the polymodal inference rules for non-commutative subexponentials. One can apply substructural
 rules only if there is the relevant index on the current modality. Also, the right introduction rule is a sort of the
-generalised right $\Box$-introduction a la $K4$.
-Modality $!_s$ might be introduced on the right only if its index is less than any other subexponential index from the antecedent.
-That is, if we have already used stronger modality, then we may
-apply the weaker one.
+generalised right $\Box$-introduction a la the modal logic ${\bf K}4$. Modality $!_s$ might be introduced on the right only if its index is less than any other
+subexponential index from the antecedent. That is, if we have already used stronger modality, then we may apply the weaker one.
 
@@
 The first of all, the cut rule is admissible. Generally, this calculus is undecidable, but the fragment without non-local
-contraction is PSPACE-complete. These results were obtained by Kanovich, Kuznetsov, Nigam, and Scedrov \cite{Sc}.
+contraction is PSPACE. These results were obtained by Kanovich, Kuznetsov, Nigam, and Scedrov \cite{Sc}.
 
@@
 \begin{itemize}
-\item Let $A$ be a semigroup (monoid), then $\langle \mathcal{P}(A), \cdot, \subseteq \rangle$
+\item Let $S$ be a semigroup (monoid), then $\langle \mathcal{P}(S), \cdot, \subseteq \rangle$
 is a free (unital) quantale.
-\item Let $R$ be a ring and $Sub(R)$ be a set of additive subgroups of $R$.
+\item Let $\mathcal{R}$ be a ring and $Sub(\mathcal{R})$ be a set of additive subgroups of $R$.
 We define $A \cdot B$ as an additive subgroup generated by finite sums of products $ab$ and order is defined by inclusion.
@@
 Then, if $f : \mathcal{Q}_1 \to \mathcal{Q}_2$ is a quantale homomorphism, then $f(\mathcal{S}) \subseteq \mathcal{Q}_2$ is a subquantale of $\mathcal{Q}_2$.
+
+That is, a homomorphic image of subquatale is a subquantale.
 \end{prop}
@@
 
-  Follows from the same statements for semigroup and semilattice homomorphisms.
+  Obviously.
 \end{proof}
@@
 
-  \item A quantic conucleus is called unital, if $\forall a \in Q, \Box a \leq e$.
+  \item A quantic conucleus is called unital, if $\forall a \in Q, I a \leq e$.
 \end{enumerate}
@@
   \begin{enumerate}
-    \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then $I : \mathcal{Q} \to \mathcal{Q}$, such that $\Box a = \bigvee \{ s \in S \: | \: s \leq a \}$, is an open modality.
+    \item Let $S \subseteq \mathcal{Q}$ be a subquantale, then the operation $I : \mathcal{Q} \to \mathcal{Q}$, such that $I a = \bigvee \{ q \in S \: | \: q \leq a \}$, is an open modality.
     \item Let $S_1$ and $S_2$ are subquantales such that $\mathcal{S}_1 \subseteq \mathcal{S}_2 \subseteq \mathcal{Q}$.
@@
 
-\begin{lemma} Let $I$ be a quantic conucleus, then for all $a \in \mathcal{Q}$, $I a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$, where $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$.
+\begin{lemma} Let $I$ be a quantic conucleus, then for all $a \in \mathcal{Q}$, $I a = \bigvee \{ q \in Q_{I} \: | \: q \leq a \}$, where $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$.
 \end{lemma}
@@
 
-So far as $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$ is a subquantale, then $I' a = \bigvee \{ q \in Q_{I} \: | \: s \leq a \}$ is a quantic conucleus.
+So far as $Q_{I} = \{ a \in \mathcal{Q} \: | \: I a = a \}$ is a subquantale, then $I' a = \bigvee \{ q \in Q_{I} \: | \: q \leq a \}$ is a quantic conucleus.
 Let us show that these operations are equavalent.
@@
 $\begin{array}{lll}
-&\bigvee \{ q \in Q_{I} \: | \: s \leq a \} = & \\
+&\bigvee \{ q \in Q_{I} \: | \: q \leq a \} = & \\
 & \:\:\:\:\:\:\:\: \text{$s \in Q_{I}$, so s is a fixpoint of $I$} & \\
-&\bigvee \{ q \in Q_{I} \: | \: I s \leq a \} = & \\
+&\bigvee \{ q \in Q_{I} \: | \: I q \leq a \} = & \\
 & \:\:\:\:\:\:\:\: \text{By equivalence}& \\
-&\bigvee \{ q \in Q_{I} \: | \: I s \leq I a \} = & \\
+&\bigvee \{ q \in Q_{I} \: | \: I q \leq I a \} = & \\
 & \:\:\:\:\:\:\:\: \text{By fixpoint} & \\
-&\bigvee \{ q \in Q_{I} \: | \: s \leq I a \} \leq I a& \\
+&\bigvee \{ q \in Q_{I} \: | \: q \leq I a \} \leq I a& \\
 \end{array}$
@@
 \begin{enumerate}
-  \item $I a = \bigvee \{ s \in S \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \}$ is a central quantic conucleus
-  \item $I a = \bigvee \{ s \in S \: | \: s \leq a, s \leq \mathds{1} \}$ is an unital conucleus
-  \item $I a = \bigvee \{ s \in S \: | \: s \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$ is a generalised square-increasing quantic conucleus
+  \item $I a = \bigvee \{ q \in S \: | \: q \leq a, q \in \mathcal{Z}(\mathcal{Q}) \}$ is a central quantic conucleus
+  \item $I a = \bigvee \{ q \in S \: | \: q \leq a, q \leq \mathds{1} \}$ is an unital conucleus
+  \item $I a = \bigvee \{ q \in S \: | \: q \leq a, \forall b \in Q, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s\}$ is a generalised square-increasing quantic conucleus
   \item Operations with combinations of conditions above
@@
   $\sigma(s_i) = \begin{cases}
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a\},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ q \in S_i \: | \: q \leq a\},
   \\ \:\:\:\: \text{if $s_i \notin W \cap C \cap E$} \\
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ q \in S_i \: | \: q \leq a, q \leq \mathds{1}\},
   \\ \:\:\:\: \text{if $s_i \in W$} \\
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ q \in S_i \: | \: q \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
   \\ \:\:\:\: \text{if $s_i \in E$} \\
-  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
+  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ q \in S_i \: | \: q \leq a, \forall b, b \cdot q \vee q \cdot b \leq q \cdot b \cdot s \},
   \\ \:\:\:\: \text{if $s_i \in E$} \\
@@
 
-\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : I \to CN(\mathcal{Q})$ a subexponential interpretation, then interpretation is defined inductively:
+\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : \Sigma \to CN(\mathcal{Q})$ a subexponential interpretation, then interpretation is defined inductively:
 
@@
 
-\begin{prop} $s \in A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$ iff $\sigma(s)$ is a unital (central or square increasing) modality.
+\begin{prop} $s \in A = \mathcal{W}, \mathcal{C}, \mathcal{E}$ iff $\sigma(s)$ is a unital (central or square increasing) modality.
 \end{prop}
@@
   In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
-  \item Let $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$, then $A$ is downwardly closed
-  $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
+  \item Let $A = \mathcal{W}, \mathcal{C}, \mathcal{E}$, then $A$ is downwardly closed
+  $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed.
   \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
